---
title: "bilatsim"
author: "DVM Bishop and Paul Thompson"
date: "25/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggpubr") #for ggdensity function
require(tidyverse)
library(cowplot)
library(diptest)
library(ggpubr)
library(knitr)
library(kableExtra)
library(matrixStats)
library(janitor)

library(propagate)
```

## Rationale

If we find that the average LI on a task (such as Jabberwocky) is zero, this could mean one of 2 things.
A) both sides of the brain participate equally in the task in all people
B) the population is composed of a 50:50 mix of people who are left vs right-lateralised on the task (to a greater or lesser extent)

I think in the literature on laterality, A is generally assumed. But I think our data show B.

Simulation 1: simulating distribution of categorical laterality if the true situation is bilateral activation.
So 
1. simulate LI for individual trials as a random normal deviate with mean zero and SD 1
2. compute SE for the LI scores for each session
3. categorise each case as L, Bilateral, R depending on whether the CI crosses zero
4. consider the distribution of categories for the 2 sessions together

```{r simLI}

simLI<-function(sim_type='B',npartic=1000,mymean=0,ntrial=15,TRT=0.7,SD_t1=0.5,SD_t2=0.8)
{
  library(matrixStats)
#npartic=1000 #Large N participants simulated so can see distribution of laterality categories
#nsess=2 #2 sessions

mysim <- data.frame(matrix(NA,nrow=npartic,ncol=5))
colnames(mysim)<-c('Subject','LI_t1','LI_t2','SE_t1','SE_t2') #,'lowCI','hiCI','Cat','Cat2')
#ntrial <- 15 #n trials for each session
thisrow<-0 #row counter for the data frame; incremented for each participant/session

for (p in 1:npartic){
  mysim$Subject[p]<-p
  #It's really interesting to vary the value of mymean to see the effect!
if(sim_type=='B')
{
  #use runif to in effect throw a dice and flip sign on the effect for 50% of trials
if (runif(1)<.5) {mymean <- mymean*-1}
}
else{mymean<-0}
  
# PT: I have had to change the way that DB simulated the data to allow for the test-retest (TRT) correlation between the time points. The data is simulated in short form then change to long format and we can remove one loop and vectorise some calcs.
myCorMat<-matrix(c(1,TRT,TRT,1),2,2,byrow=TRUE)
mySigma <- propagate::cor2cov(myCorMat,var=c(SD_t1^2,SD_t1^2)) #convert correlation matrix to covariance matrix to allow jabberwocky dist to have different variance from 1 and allow unequal variance (possible, but unlikely).   
  
LItrial <- MASS::mvrnorm(ntrial,c(mymean,mymean),Sigma=mySigma) #ntrial random normal deviates with mean mymean, SD = 1, and corr = TRT (see arguement inputs.

mysim[p,c('LI_t1','LI_t2')] <- base::colMeans(LItrial)  #LI for that session is mean of individual trial LIs
mysim[p,c('SE_t1','SE_t2')] <- matrixStats::colSds(LItrial)/sqrt(ntrial) #standard error for session LIs
}

mysim <- mysim %>% gather(key='ref',value='value',-Subject) %>% extract('ref',c('ref','Session'),"([[:alnum:]]+)_([[:alnum:]]+)")%>% spread('ref','value') 


mysim$lowCI <- with(mysim,LI - 1.96*SE) #95% CI lower bound for mean LI
mysim$hiCI <- with(mysim,LI + 1.96*SE) #95% CI upper bound for mean LI
#now categorise the mean LI for session as 1 = right, 2 = bilateral, 3 = left
mysim$Cat<-2  #bilateral is the default

for(j in 1:dim(mysim)[1]){

if (mysim$hiCI[j]<0) {
  mysim$Cat[j] <-1} #R lateralised if top range of CI is below zero
if (mysim$lowCI[j]>0) {
  mysim$Cat[j] <-3} #L lateralised if bottom range of CI is above zero
}

mysimCat2<-mysim %>%
   group_by(Subject) %>%
   summarise(Cat2 = paste(Cat, collapse=''))

mysim$Cat2<-c(sapply(mysimCat2$Cat2, function(x) c(NA,x)))


#Now create 2 digit category (e.g. 12, 22, 32) representing category for session 1 + session 2
#This will be just recorded in the row for session 2
# mysim$Cat2<-rep(NA,length=dim(mysim)[1])
# if (mysim$time=='t2'){
#   mysim$Cat2[j]<-10*mysim$Cat[(j-1)]+mysim$Cat[thisrow]
#   mysim$CatSD2[j]<-10*mysim$CatSD[(thisrow-1)]+mysim$CatSD[thisrow]
# }


return(mysim)
}

means=c(0,0.2,0.4)
mysimA <- simLI(sim_type='A',npartic=1000,mymean=0,ntrial=15,TRT=0.85,SD_t1=0.8,SD_t2=0.5)


for(i in means)
{
  nam<-paste0("mysimB_",i)
assign(nam,simLI(sim_type='B',npartic=1000,mymean=i,ntrial=15,TRT=0.85,SD_t1=0.8,SD_t2=0.5))
}

```

```{r freq_tables_sim}
tabyl(mysimA$Cat2, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)

tabyl(mysimB_0$Cat2, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)

tabyl(mysimB_0.2$Cat2, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)

tabyl(mysimB_0.4$Cat2, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

```{r dist_sims}
 ggplot(mysimA,aes(x=LI))+geom_density(aes(fill=as.factor(Session),group=as.factor(Session)),alpha=0.5)+theme_bw()+ guides(fill=guide_legend(title="Session"))+theme(legend.position='top')

```

This has really clarified 2 things for me.
First, as I expected, if we are drawing from a population of values where true mean is zero, then it is not uncommon to find some cases where the category is bilateral in one session and either L or R in the other session (red values). About 16% of values are red.
But it is vanishingly rare to find cases where the categorisation is LL, LR or RR.

Second, if invididual people really are unlateralised, so drawn from a population with a mean of zero for the LI, then test-retest reliability of the LI will be zero. This is because the only reason for an estimate of LI deviating from zero would be chance.
I had an intuition this should be the case, which was why I was getting excited about the good test-retest reliability of Jabberwocky. You'd only see that if there was meaningful individual variation in the LI - i.e. although the group mean is zero, the people in the group are reliably left- or right-lateralised.

Now let's try simulating model B

Can use same script - all that changes is the way the random normal deviate is specified.
In half the people, you have a mean less than zero, and in half a mean greater than zero.
The results will depend on how large the difference is from zero



```{r dist_sims2,warning=FALSE,message=FALSE}
p1<-ggplot(mysimB_0,aes(x=LI))+geom_density(aes(fill=as.factor(Session),group=as.factor(Session)),alpha=0.5)+theme_bw()+ guides(fill=guide_legend(title="Session"))+theme(legend.position='top')+ggtitle(paste0("Model B: meanbias = ",0))

p2<-ggplot(mysimB_0.2,aes(x=LI))+geom_density(aes(fill=as.factor(Session),group=as.factor(Session)),alpha=0.5)+theme_bw()+ guides(fill=guide_legend(title="Session"))+theme(legend.position='top')+ggtitle(paste0("Model B: meanbias = ",0.2))

p3<-ggplot(mysimB_0.4,aes(x=LI))+geom_density(aes(fill=as.factor(Session),group=as.factor(Session)),alpha=0.5)+theme_bw()+ guides(fill=guide_legend(title="Session"))+theme(legend.position='top')+ggtitle(paste0("Model B: meanbias = ",0.4))

ggpubr::ggarrange(p1,p2,p3,ncol=2,nrow=2,common.legend=TRUE)

```




```{r simscatterplots,warning=FALSE,message=FALSE}
mysim2 <- data.frame(Session1=mysimA$LI[mysimA$Session=='t1'],Session2=mysimA$LI[mysimA$Session=='t2'],Cols = mysimA$Cat2[mysimA$Session=='t2'])

mysim2$Cols <- car::recode(mysim2$Cols,"22='bilateral on both sessions';11='same lateralised in both sessions';33='same lateralised in both sessions';12='bilateral in one session';21='bilateral in one session';23='bilateral in one session';32='bilateral in one session';13='lateralised in opposite direction in each session';31='lateralised in opposite direction in each session'")
library(ggpubr)
mysim2$Cols<-as.factor(mysim2$Cols)
# Scatter plot colored by groups ("Species")
sp <- ggscatter(mysim2, x = "Session1", y = "Session2",
            color = "Cols", palette = "jco",
            size = 2, alpha = 0.6)+
border()                                         
# Marginal density plot of x (top panel) and y (right panel)
xplot <- ggdensity(mysim2, "Session1", fill = "Cols",
               palette = "jco")
yplot <- ggdensity(mysim2, "Session2", fill = "Cols", 
               palette = "jco")+
rotate()
# Cleaning the plots
sp <- sp + rremove("legend")
yplot <- yplot + clean_theme() + rremove("legend") 
xplot <- xplot + clean_theme() + rremove("legend")
# Arranging the plot using cowplot
library(cowplot)
plot_grid(xplot, NULL, sp, yplot, ncol = 2, align = "hv", 
      rel_widths = c(2, 1), rel_heights = c(1, 2))

```

```{r simscatterplots2,warning=FALSE,message=FALSE}
mysimB00 <- data.frame(Session1=mysimB_0$LI[mysimB_0$Session=='t1'],Session2=mysimB_0$LI[mysimB_0$Session=='t2'],Cols = mysimA$Cat2[mysimB_0$Session=='t2'])
mysimB02 <- data.frame(Session1=mysimB_0.2$LI[mysimB_0.2$Session=='t1'],Session2=mysimB_0.2$LI[mysimB_0.2$Session=='t2'],Cols = mysimB_0.2$Cat2[mysimB_0.2$Session=='t2'])
mysimB04 <- data.frame(Session1=mysimB_0.4$LI[mysimB_0.4$Session=='t1'],Session2=mysimB_0.4$LI[mysimB_0.4$Session=='t2'],Cols = mysimB_0.4$Cat2[mysimB_0.4$Session=='t2'])



sim_scatter <- function(mysim2=mysimB00)
{

mysim2$Cols <- car::recode(mysim2$Cols,"22='bilateral on both sessions';11='same lateralised in both sessions';33='same lateralised in both sessions';12='bilateral in one session';21='bilateral in one session';23='bilateral in one session';32='bilateral in one session';13='lateralised in opposite direction in each session';31='lateralised in opposite direction in each session'")
library(ggpubr)
mysim2$Cols<-as.factor(mysim2$Cols)
# Scatter plot colored by groups ("Species")
sp <- ggscatter(mysim2, x = "Session1", y = "Session2",
            color = "Cols", palette = "jco",
            size = 2, alpha = 0.6)+
border()                                         
# Marginal density plot of x (top panel) and y (right panel)
xplot <- ggdensity(mysim2, "Session1", fill = "Cols",
               palette = "jco")
yplot <- ggdensity(mysim2, "Session2", fill = "Cols", 
               palette = "jco")+
rotate()
# Cleaning the plots
sp <- sp + rremove("legend")
yplot <- yplot + clean_theme() + rremove("legend") 
xplot <- xplot + clean_theme() + rremove("legend")
# Arranging the plot using cowplot
library(cowplot)


g1<-plot_grid(xplot, NULL, sp, yplot, ncol = 2, align = "hv", 
      rel_widths = c(2, 1), rel_heights = c(1, 2))
return(g1)
}
```

```{r scatter_B0,message=FALSE,warning=FALSE,fig.cap='Mean bias = 0'}
sim_scatter(mysimB00)
```

```{r scatter_B02,message=FALSE,warning=FALSE,fig.cap='Mean bias = 0.2'}
sim_scatter(mysimB02)
```

```{r scatter_B04,message=FALSE,warning=FALSE,fig.cap='Mean bias = 0.4'}
sim_scatter(mysimB04)
```


This confirms that model B can explain the fact that significant numbers of individuals are categorised as LL or RR (ie 11 or 33), though most are still BB (22)
And it can explain why we have a positive correlation between the two sessions.



# Comparison with real data
Use A2 + Bangor data from Laterality_paper_analyses_Mar2020.rmd

```{r A2dataplus}
library(janitor)
myA2<-read.csv('all_LI_lat.csv')

myA2_left<-myA2[myA2$handedness=='L',]
myA2_right<-myA2[myA2$handedness=='R',]
#Focus on Jabberwocky as the least lateralised task

tabyl(myA2_left$Jabber12, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)


tabyl(myA2_right$Jabber12, sort = TRUE) %>% mutate(percent=round(percent*100,2)) %>% select(1:3) %>% kable(col.names = c("Laterality category","N","Percent")) %>% kable_styling(bootstrap_options = "striped", full_width = F)


```



```{r plots_left}
myA2_left2<-myA2_left[is.na(myA2_left$Jabber12)==FALSE,]
myA2_left2$Jabber12<-as.factor(myA2_left2$Jabber12)
myA2_left2$Jabber12<-recode_factor(myA2_left2$Jabber12, `22` = "bilateral both", `11` = "both lateralised", `33` = "both lateralised", `12`="bilateral in one session", `21`="bilateral in one session", `23`="bilateral in one session", `32`="bilateral in one session", `13`="opposite lateralisations", `31`="opposite lateralisations")
# Main plot
pmain <- ggplot(myA2_left2, aes(x = Jabber1, y = Jabber2, color = Jabber12))+
  geom_point()+ggpubr::color_palette("jco")+annotate('text',2,-2,label=paste0('r = ',round(cor(myA2_left$Jabber1,myA2_left$Jabber2,use='complete.obs'),2)))+theme_bw() + guides(color=guide_legend(title="Laterality class"))+ rremove("legend") 
# Marginal densities along x axis
xdens <- axis_canvas(pmain, axis = "x")+
  geom_density(data = myA2_left2, aes(x = Jabber1, fill = Jabber12),
              alpha = 0.7, size = 0.2)+
  ggpubr::fill_palette("jco")
# Marginal densities along y axis
# Need to set coord_flip = TRUE, if you plan to use coord_flip()
ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
  geom_density(data = myA2_left2, aes(x = Jabber2, fill = Jabber12),
                alpha = 0.7, size = 0.2)+
  coord_flip()+
  ggpubr::fill_palette("jco")
p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
g1<-ggdraw(p2)

```


```{r plots_right}
myA2_right2<-myA2_right[is.na(myA2_right$Jabber12)==FALSE,]
myA2_right2$Jabber12<-as.factor(myA2_right2$Jabber12)
myA2_right2$Jabber12<-recode_factor(myA2_right2$Jabber12, `22` = "bilateral both", `11` = "both lateralised", `33` = "both lateralised", `12`="bilateral in one session", `21`="bilateral in one session", `23`="bilateral in one session", `32`="bilateral in one session", `13`="opposite lateralisations", `31`="opposite lateralisations")
# Main plot
pmain <- ggplot(myA2_right2, aes(x = Jabber1, y = Jabber2, color = Jabber12))+
  geom_point()+ggpubr::color_palette("jco")+annotate('text',2,-2,label=paste0('r = ',round(cor(myA2_right$Jabber1,myA2_right$Jabber2,use='complete.obs'),2)))+theme_bw() + guides(color=guide_legend(title="Laterality class"))+ rremove("legend") 
# Marginal densities along x axis
xdens <- axis_canvas(pmain, axis = "x")+
  geom_density(data = myA2_right2, aes(x = Jabber1, fill = Jabber12),
              alpha = 0.7, size = 0.2)+
  ggpubr::fill_palette("jco")
# Marginal densities along y axis
# Need to set coord_flip = TRUE, if you plan to use coord_flip()
ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
  geom_density(data = myA2_right2, aes(x = Jabber2, fill = Jabber12),
                alpha = 0.7, size = 0.2)+
  coord_flip()+
  ggpubr::fill_palette("jco")
p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
g2<-ggdraw(p2)
```


```{r plot_both}
ggarrange(g1,g2,ncol=2,nrow=1,labels=c('LEFT','RIGHT'))
```