---
title: "Laterality_Paper2-power"
author: "Zoe Woodhead & Paul Thompson"
date: "28/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Set variables and load packages

```{r settings, warning=FALSE, message=FALSE}

require(tidyverse)
library(MASS)
options(scipen=999)
```


# Structural Equation Modeling

## Simulate data

```{r sim_dat}
#========================================================================#
# simulate multivariate normal data to test ESEM model on three outcomes.#
#========================================================================#

sim_data<-function(n=300)
{

sig1 <- matrix(c(1,	0.7,	0,	0,	0,	0,
                 0.7, 1, 0, 0, 0, 0,
                 0, 0, 1, 0.7, 0, 0,
                 0, 0, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_null <- mvrnorm(n=n, mu = c(5,5,5,5,5,5), Sigma=sig1)

#========================================================================#

sig2 <- matrix(c(1,	0.7,	0.4,	0.4,	0,	0,
                 0.7, 1, 0.4, 0.4, 0, 0,
                 0.4, 0.4, 1, 0.7, 0, 0,
                 0.4, 0.4, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_language <- mvrnorm(n=n, mu = c(5,5,5,5,5,5), Sigma=sig2)

#========================================================================#

sig3 <- matrix(c(1,	0.7, 0.4,	0.4, 0.4, 0.4,
                 0.7, 1, 0.4, 0.4, 0.4, 0.4,
                 0.4, 0.4, 1, 0.7, 0.4, 0.4,
                 0.4, 0.4, 0.7, 1, 0.4, 0.4,
                 0.4,0.4,0.4,0.4,1,0.7,
                 0.4,0.4,0.4,0.4,0.7,1),6,6,byrow=TRUE)

data_genLAT <- mvrnorm(n=n, mu = c(5,5,5,5,5,5), Sigma=sig3)

#========================================================================#

data_null<-as.data.frame(data_null)
data_language<-as.data.frame(data_language)
data_genLAT<-as.data.frame(data_genLAT)

names(data_null)<-names(data_language)<-names(data_genLAT)<-c("dichotic1","dichotic2","rhyme1","rhyme2","faces1","faces2")

data_null<-data_null[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_language<-data_language[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_genLAT<-data_genLAT[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]

return(list(data_null=data_null,data_language=data_language,data_genLAT=data_genLAT))
}
#========================================================================#
```

## Roger Kievit's suggestion - modelling data with three prespecified covariance structures, then compare using AIC weights.

This is a subset of SEM that dos not include any latent variables or directional paths. It only looks to constrain particular covariance patterns and report 'best' model according AIC weights.

```{r Roger_mod}
library(lavaan)
library(qpcR)
library(tidyverse)
library(semPlot)

sem_pwr_cov<-function(n=300,Niters=100)
{

  LLR_testB <- vector(mode="numeric", length=100)
  LLR_testC <- vector(mode="numeric", length=100)
  
  for(i in 1:Niters)
{
sims <- sim_data(n=n)

model1<-"
dichotic1~~0*rhyme1
dichotic1~~0*faces1 
rhyme1~~0*faces1 
"

model2<-"
dichotic1~~rhyme1 
dichotic1~~0*faces1
rhyme1~~0*faces1 
"

model3<-"
dichotic1~~rhyme1 
dichotic1~~faces1 
rhyme1~~faces1
"

fit1A <- cfa(model1, data=sims$data_null)
fit2A <- cfa(model2, data=sims$data_null)
fit3A <- cfa(model3, data=sims$data_null)

#aic_vector1 <- c(fitMeasures(fit1A, "aic"),fitMeasures(fit2A, "aic"),fitMeasures(fit3A, "aic"))

fit1B <- cfa(model1, data=sims$data_language)
fit2B <- cfa(model2, data=sims$data_language)
fit3B <- cfa(model3, data=sims$data_language)

#aic_vector2 <- c(fitMeasures(fit1B, "aic"),fitMeasures(fit2B, "aic"),fitMeasures(fit3B, "aic"))

fit1C <- cfa(model1, data=sims$data_genLAT)
fit2C <- cfa(model2, data=sims$data_genLAT)
fit3C <- cfa(model3, data=sims$data_genLAT)

# aic_vector3 <- c(fitMeasures(fit1C, "aic"),fitMeasures(fit2C, "aic"),fitMeasures(fit3C, "aic"))
# 
# 
# AICweights1<-akaike.weights(aic_vector1)$weights
# AICweights2<-akaike.weights(aic_vector2)$weights
# AICweights3<-akaike.weights(aic_vector3)$weights
# 
# IC_objectweights1<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights1)
# IC_objectweights2<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights2)
# IC_objectweights3<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights3)

LLR_testB[i] <- anova(fit1B,fit2B,fit3B)$`Pr(>Chisq)`[3]
LLR_testC[i] <- anova(fit1C,fit2C,fit3C)$`Pr(>Chisq)`[3]
}

LLR_testB_ind<-ifelse(LLR_testB>=0.05,0,1)
LLR_testC_ind<-ifelse(LLR_testC>=0.05,0,1)
  
hyp1_pwr = mean(LLR_testB_ind)
hyp2_pwr = mean(LLR_testC_ind)

return(list(hypothesis1_pwr=hyp1_pwr,hypothesis2_pwr=hyp2_pwr,LLR_testB=LLR_testB,LLR_testC=LLR_testC))
}

sem_pwr_cov(n=80,Niters=100)

```
