---
title: "Laterality_Paper2"
author: "Zoe Woodhead & Paul Thompson"
date: "13/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Set variables and load packages

```{r settings, warning=FALSE, message=FALSE}

require(tidyverse)
library(MASS)
```


# Structural Equation Modeling

## Simulate data

```{r sim_dat}
#========================================================================#
# simulate multivariate normal data to test ESEM model on three outcomes.#
#========================================================================#



sig1 <- matrix(c(1,	0.7,	0,	0,	0,	0,
                 0.7, 1, 0, 0, 0, 0,
                 0, 0, 1, 0.7, 0, 0,
                 0, 0, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_null <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig1)

#========================================================================#

sig2 <- matrix(c(1,	0.7,	0.4,	0.4,	0,	0,
                 0.7, 1, 0.4, 0.4, 0, 0,
                 0.4, 0.4, 1, 0.7, 0, 0,
                 0.4, 0.4, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_language <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig2)

#========================================================================#

sig3 <- matrix(c(1,	0.7, 0.4,	0.4, 0.4, 0.4,
                 0.7, 1, 0.4, 0.4, 0.4, 0.4,
                 0.4, 0.4, 1, 0.7, 0.4, 0.4,
                 0.4, 0.4, 0.7, 1, 0.4, 0.4,
                 0.4,0.4,0.4,0.4,1,0.7,
                 0.4,0.4,0.4,0.4,0.7,1),6,6,byrow=TRUE)

data_genLAT <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig3)

#========================================================================#

data_null<-as.data.frame(data_null)
data_language<-as.data.frame(data_language)
data_genLAT<-as.data.frame(data_genLAT)

names(data_null)<-names(data_language)<-names(data_genLAT)<-c("dichotic1","dichotic2","rhyme1","rhyme2","faces1","faces2")

data_null<-data_null[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_language<-data_language[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_genLAT<-data_genLAT[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]

#========================================================================#
```

## Roger Kievit's suggestion - modelling data with three prespecified covariance structures, then compare using AIC weights.

This is a subset of SEM that dos not include any latent variables or directional paths. It only looks to constrain particular covariance patterns and report 'best' model according AIC weights.

```{r Roger_mod}
library(lavaan)
library(qpcR)
library(tidyverse)
library(semPlot)

model1<-"
dichotic1~~0*rhyme1
dichotic1~~0*faces1 
rhyme1~~0*faces1 
"

model2<-"
dichotic1~~rhyme1 
dichotic1~~0*faces1
rhyme1~~0*faces1 
"

model3<-"
dichotic1~~rhyme1 
dichotic1~~faces1 
rhyme1~~faces1
"

fit1A <- cfa(model1, data=data_null)
fit2A <- cfa(model2, data=data_null)
fit3A <- cfa(model3, data=data_null)

aic_vector1 <- c(fitMeasures(fit1A, "aic"),fitMeasures(fit1A, "aic"),fitMeasures(fit1A, "aic"))

fit1B <- cfa(model1, data=data_language)
fit2B <- cfa(model2, data=data_language)
fit3B <- cfa(model3, data=data_language)

aic_vector2 <- c(fitMeasures(fit1B, "aic"),fitMeasures(fit2B, "aic"),fitMeasures(fit3B, "aic"))

fit1C <- cfa(model1, data=data_genLAT)
fit2C <- cfa(model2, data=data_genLAT)
fit3C <- cfa(model3, data=data_genLAT)

aic_vector3 <- c(fitMeasures(fit1C, "aic"),fitMeasures(fit2C, "aic"),fitMeasures(fit3C, "aic"))

# summary(fit1A, fit.measures=TRUE)
# summary(fit2A, fit.measures=TRUE)
# summary(fit3A, fit.measures=TRUE)
# 
# summary(fit1B, fit.measures=TRUE)
# summary(fit2B, fit.measures=TRUE)
# summary(fit3B, fit.measures=TRUE)
# 
# summary(fit1C, fit.measures=TRUE)
# summary(fit2C, fit.measures=TRUE)
# summary(fit3C, fit.measures=TRUE)

AICweights1<-akaike.weights(aic_vector1)$weights
AICweights2<-akaike.weights(aic_vector2)$weights
AICweights3<-akaike.weights(aic_vector3)$weights

IC_objectweights1<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights1)
IC_objectweights2<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights2)
IC_objectweights3<-data.frame(Model=factor(rep(c('Model 1','Model 2','Model 3'))), IC = factor(rep('AIC',each=3)),values=AICweights3)

ggplot(IC_objectweights1,aes(Model,values,fill=Model))+geom_bar(stat='identity',position="dodge")+ylab('Akaike weights') + theme_bw()

semPaths(fit1A, "std")

ggplot(IC_objectweights2,aes(Model,values,fill=Model))+geom_bar(stat='identity',position="dodge")+ylab('Akaike weights') + theme_bw()

semPaths(fit2B, "std")

ggplot(IC_objectweights3,aes(Model,values,fill=Model))+geom_bar(stat='identity',position="dodge")+ylab('Akaike weights') + theme_bw()

semPaths(fit3C, "std")

```
