---
title: "Laterality_Paper"
author: "Zoe Woodhead"
date: "20/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This script reads in data from A2 study (from dropbox) and new data acquired at Bangor (stored locally), and performs basic summary statistics followed by SEM analysis of the laterality indices.

*Before you start*
The following files need to downloaded from OSF (https://osf.io/qetj5/files/) and saved to the working directory:

*A2_Participant_Info_Bangor.csv
*Bangor_Results_Session1.csv
*Bangor_Results_Session2.csv
*A2_Behavioural_Data_Bangor.csv
The following script needs to be pulled from github:
*geom_pirate_ZW.R
The following package needs to be installed manually:
*devtools::install_github("mikabr/ggpirate")

## Set variables and load packages

```{r settings, warning=FALSE, message=FALSE}
########### Set toggles before running! ################################################################

# These toggles determine the parameters used in the analysis
Fonly             <- 0 # Set to 1 for females only. MANUSCRIPT SETTING = 0
Init30only        <- 0 # Set to 1 to include just the initial preregistered group (23 R and 7 L hander). MANUSCRIPT SETTING = 0
tryreorder        <- 1 # Set to 1 to change the fixed path in the SEM model. MANUSCRIPT SETTING = 1
nuorder           <-   # Sets the new order of tasks. The task listed first (and seventh) will be fixed.
 c(4,1,2,3,5,6,10,7,8,9,11,12) # Sentence generation fixed. MANUSCRIPT SETTING: c(4,1,2,3,5,6,10,7,8,9,11,12)
remove.Ntrial     <- 1 # Set to 1 to run exclusion of those with < 12 good trials. MANUSCRIPT SETTING = 1

########################################################################################################

#Needs OpenMx, which you get with following command (not CRAN)
#source('https://openmx.ssri.psu.edu/software/getOpenMx.R')
require(tidyverse)
require(OpenMx)
require(umx)
require(semTools) #for fit measures
#library(DiagrammeR) #for the diagram
require(stringr)
require(data.table)
library('devtools')
library("reshape2")
library("yarrr")
#library(DiagrammeRsvg)
library(magrittr)
library(svglite)
library(rsvg)
library(knitr)
library(dmm) #added for 'unfactor' command : nb this messes up some dplyr commands, need to specify dplyr explicitly, e.g. dplyr::select for 'select' command.
# On first use, please also install ggpirate as follows:
# devtools::install_github("mikabr/ggpirate")
library(ggpirate)
library(heplots)
```

## Read in list of participants, drop those with incomplete data

```{r participants}
particdat_A2    <- read.csv('https://osf.io/5jt6q/download')
particdat_Bangor<- read.csv('A2_Participant_Info_Bangor.csv',header=TRUE) 

incomplete <- which(particdat_Bangor$Complete == 0)
nincomplete <- length(incomplete)
cat(paste(nincomplete, ' incomplete datasets excluded from analysis'))
particdat_Bangor <- particdat_Bangor[-incomplete, ]

new_subjects <- length(particdat_Bangor$ID)
new_group_info <- particdat_Bangor %>% group_by(handedness) %>% summarise(n=n())
cat(paste('\nCompete datasets from Bangor by group: '))
new_group_info

# Merge both datasets
particdat <- rbind(particdat_A2[,c(1:4)], particdat_Bangor[,c(1:4)])
rhanded <- which(particdat$handedness == 'R')

# Create variable 'handcode', needed when numeric value used for colour in plots
particdat$handcode <- 2
particdat$handcode[rhanded] <- 1

# Create variable 'study', according to whether the data was acquired in A2 study or in Bangor
particdat$study <- c(rep('A2', length(particdat_A2$ID)), rep('Bangor', length(particdat_Bangor$ID)))

# Init30only: original sample from prereg analysis
if (Init30only==1) {
  cat('First 30 subjects only included in analysis')
  particdat<-particdat[1:30,]
}

# Fonly: only female participants
if (Fonly== 1){
  cat('Females only included in analysis')
  particdat <- filter(particdat,Gender=='F')
}

# Full datasets before excluding data:
n_full_subj <- length(particdat$ID)
full_group_info <- particdat %>% group_by(handedness) %>% summarise(n=n())
cat(paste('\nCompete datasets from both sites combined: '))
full_group_info

full_gender_info <- particdat %>% group_by(handedness, Gender) %>% summarise(n=n())
full_gender_info
```

## Read in LI data, drop those with insufficient number of good trials

During the fTCD data collection, noise may occur due to movement or interference affecting the ultrasound probes. Trials with excessive noise have been manually identified and excluded from analysis. Trials may also have been excluded if the participant failed to perform the task correctly.
There are 15 trials per task (in each session). If a participant has less than 10 'good' (included) trials for a particular task, their data for that task will be excluded from the analysis.
If a participant has missing data for more than one task, that participant will be excluded from the analysis entirely.

```{r readdata, warning=FALSE}
#read in data from sessions 1 and 2, having saved as .csv
#NB. Need to set working directory to location of data files - or else specify path
data1_A2 <- read.csv('https://osf.io/afv4h/download')
data2_A2 <- read.csv('https://osf.io/hzswc/download')

data1_Bangor <- read.csv('Bangor_Results_Session1.csv',stringsAsFactors=FALSE) #changed from read.csv to avoid creating factors!
data2_Bangor <- read.csv('Bangor_Results_Session2.csv',stringsAsFactors=FALSE)

data1 <- rbind(data1_A2, data1_Bangor)
data2 <- rbind(data2_A2, data2_Bangor)

# Only take the participants included in particdat (allows you to drop subjects by handedness, and omits incomplete subjects)
data1 <- data1[which(data1$Filename %in% particdat$ID), ] 
data2 <- data2[which(data2$Filename %in% particdat$ID), ] 

# Combine all LI data
alltask <- cbind(dplyr::select(data1, A1.LI_mean, B1.LI_mean, C1.LI_mean, D1.LI_mean, E1.LI_mean, F1.LI_mean),
                 dplyr::select(data2, A2.LI_mean, B2.LI_mean, C2.LI_mean, D2.LI_mean, E2.LI_mean, F2.LI_mean))

allN <- cbind(dplyr::select(data1, A1.N, B1.N, C1.N, D1.N, E1.N, F1.N),
              dplyr::select(data2, A2.N, B2.N, C2.N, D2.N, E2.N, F2.N))
sumN <- colSums(allN)
sumN <- sum(sumN)
total_trials <- 15*6*2*n_full_subj
dropped_trials_pc <- (total_trials - sumN) / total_trials * 100

#next loop added as R seems to think everything is a character
for (v in 1:ncol(alltask)){
  alltask[,v]<-as.numeric(alltask[,v])
}

mylabels<-c('ListGen1','PhonDec1','SemDec1','SentGen1','SentComp1','Jabber1',
            'ListGen2','PhonDec2','SemDec2','SentGen2','SentComp2','Jabber2')
myshortlab<-c('ListGen','PhonDec','SemDec','SentGen','SentComp','Jabber')
mylonglab <-c('List Generation','Phonological Decision','Semantic Decision',
              'Sentence Generation','Sentence Comprehension','Syntactic Decision')

colnames(alltask)<-mylabels

# Create a new copy where the outliers will be retained
alltaskall <- alltask

# Identify datapoints with less than 10 useable trials to be excluded
dropN<-0 #initialise counter

nbit<-c('A1.N','B1.N','C1.N','D1.N','E1.N','F1.N')
for (i in 1:6){
  w<-which(colnames(data1) == nbit[i])
  ww<-which(as.numeric(data1[ ,w]) < 10)
  if(length(ww) > 0){
    alltask[ww,i] <- NA
    dropN <- dropN + length(ww)
  }
}

nbit<-c('A2.N','B2.N','C2.N','D2.N','E2.N','F2.N')
for (i in 1:6){
  w <- which(colnames(data2) == nbit[i])
  ww <- which(as.numeric(data2[ ,w]) < 10)
  if(length(ww) > 0){
    alltask[ww,(i+6)] <- NA
    dropN <- dropN + length(ww)
    dropN
  }
}
cat(paste('Dropped datapoints because < 10 trials, N = ',dropN))

subj_inclusion <- data.frame(
  'ID' = data1$Filename,
  'include' = rep(1, length(data1$Filename))
)

for (i in 1:length(data1$Filename)){
  count_NAs <- length(which(is.na(alltask[i, ])))
  if (count_NAs > 1) { subj_inclusion$include[i] <- 0}
}

drop_subj <- subj_inclusion$ID[which(subj_inclusion$include == 0)]

cat(paste('\nDropped subjects because > 2 missing or dropped datapoints, N = ', length(drop_subj)))
cat(paste('\nDropped subject(s): ',length(drop_subj)))

# Remove these subjects from particdat, data1, data2, alltask and alltaskall
particdat <- particdat[-which(particdat$ID %in% drop_subj), ] 
alltask <- alltask[-which(data1$Filename %in% drop_subj), ]
alltaskall <- alltaskall[-which(data1$Filename %in% drop_subj), ]
data1 <- data1[-which(data1$Filename %in% drop_subj), ]
data2 <- data2[-which(data2$Filename %in% drop_subj), ]

```

## Identifying exclusions and substituting NA based on SE

After dropping tasks and subjects due to missing data (above), we now look at the standard error of the trial by trial data for each subject. If a subject has unusually high standard error for a particular task (using the Hoaglin Iglewicz criterion), their data for that task will be excluded.
Again, if a participant has excluded data for more than one task, all of the data for that participant will be excluded from the analysis.


```{r exclude, warning=FALSE}
allse <- cbind(dplyr::select(data1,A1.mean_se,B1.mean_se,C1.mean_se,D1.mean_se,E1.mean_se,F1.mean_se),
               dplyr::select(data2,A2.mean_se,B2.mean_se,C2.mean_se,D2.mean_se,E2.mean_se,F2.mean_se))

#next loop added as R seems to think everything is a character
for (v in 1:ncol(allse)){
  allse[,v]<-as.numeric(allse[,v])
}

myse<-c(allse[,1], allse[,2], allse[,3], allse[,4], allse[,5],allse[,6],
        allse[,7], allse[,8], allse[,9], allse[,10], allse[,11], allse[,12])
        
Q3<-quantile(myse,.75,na.rm=TRUE)
Q1<-quantile(myse,.25,na.rm=TRUE)
Qlimit<-Q3+2.2*(Q3-Q1)

dropSE<-0 #initialise counter

for (i in 1:12){
  w <- which(allse[,i]>Qlimit)
  if (length(w)>0){
    alltask[w,i]<-NA
    dropSE <- dropSE + length(w)
  }
}

cat(paste('Dropped datapoints because high SE, N = ',dropSE))

# Drop participants if two or more datapoints are dropped as outliers
subj_inclusion_outliers <- data.frame(
  'ID' = data1$Filename,
  'include' = rep(1, length(data1$Filename))
)

for (i in 1:length(data1$Filename)){
  count_NAs <- length(which(is.na(alltask[i, ])))
  if (count_NAs > 1) { subj_inclusion_outliers$include[i] <- 0}
}

drop_subj_outliers <- subj_inclusion_outliers$ID[which(subj_inclusion_outliers$include == 0)]

cat(paste('\nDropped subjects because > 2 outlier datapoints, N = ', length(drop_subj_outliers)))
cat(paste('\n', drop_subj_outliers))

if (length(drop_subj_outliers) > 0){
  # Remove these subjects from particdat, data1, data2, alltask and alltaskall
  particdat <- particdat[-which(particdat$ID %in% drop_subj_outliers), ] 
  alltask <- alltask[-which(data1$Filename %in% drop_subj_outliers), ]
  alltaskall <- alltaskall[-which(data1$Filename %in% drop_subj_outliers), ]
  data1 <- data1[-which(data1$Filename %in% drop_subj_outliers), ]
  data2 <- data2[-which(data2$Filename %in% drop_subj_outliers), ]
}

# Count final number of subjects
nsubj_final <- dim(data1)[1]
cat(paste('\nFinal number of subjects: ', nsubj_final))
```

Calculate laterality categories

```{r lat_cat}
# Function to calculate laterality categories from LI and SE
calculate_cat <- function(myLI, mySE){
  myside <- 1
  my_cat <- 1
  if(myLI < 0){
    myside <- -1
    my_cat <- -1
    myLI <- myLI * -1 # flip LI so test works
  }
  if((myLI - mySE*1.96) < 0){ my_cat <- 0}
  return(my_cat)
}

# Calculate laterality categories for all subjects
alltasklat <- matrix(data=NA, nrow=dim(alltask)[1], ncol = dim(alltask)[2])
for (s in 1:dim(alltask)[1]){ # subject loop
  for (t in 1:dim(alltask)[2]){ # task loop
    if (is.na(alltask[s,t]) == FALSE){
      
      my_cat <- calculate_cat(alltask[s,t], allse[s,t])
      alltasklat[s,t] <- my_cat
    }
  }
}

colnames(alltasklat)<-mylabels
alltasklat <- as.data.frame(alltasklat)
#recode so that 1 = R, 2= bilateral, 3 = left
alltasklat<-alltasklat+2

# Code consistent / inconsistent categories over time
lat_consistency <- data.frame(
  A = rep(1, length(particdat$ID)), 
  B = rep(1, length(particdat$ID)),
  C = rep(1, length(particdat$ID)),
  D = rep(1, length(particdat$ID)),
  E = rep(1, length(particdat$ID)),
  F = rep(1, length(particdat$ID))
)

lat_consistency$A[which(alltasklat$ListGen1 != alltasklat$ListGen2)] <- 0
lat_consistency$B[which(alltasklat$PhonDec1 != alltasklat$PhonDec2)] <- 0
lat_consistency$C[which(alltasklat$SemDec1 != alltasklat$SemDec2)] <- 0
lat_consistency$D[which(alltasklat$SentGen1 != alltasklat$SentGen2)] <- 0
lat_consistency$E[which(alltasklat$SentComp1 != alltasklat$SentComp2)] <- 0
lat_consistency$F[which(alltasklat$Jabber1 != alltasklat$Jabber2)] <- 0
```


## Report demographic summary statistics for all INCLUDED participants
I.e omitting participants who have been excluded from the analysis as described above.

```{r demographics}
#Participant descriptors reported in paper
n_info <- particdat %>% group_by(handedness, study, Gender) %>% summarise(n=n()) 
n_info

gender_by_handedness <- particdat %>% group_by(handedness, Gender) %>% summarise(n=n()) 
gender_table <- cbind(gender_by_handedness$n[1:2], gender_by_handedness$n[3:4])
colnames(gender_table) <- c('Left','Right')
rownames(gender_table) <- c('Female','Male')
chisq.test(gender_table)


age_info <- particdat %>% summarise(age_mean = mean(Age_m)/12, age_sd = sd(Age_m)/12)
print(age_info)

# Do left / right participants differ in age
t.test(particdat$Age_m[which(particdat$handcode==1)], particdat$Age_m[which(particdat$handcode==2)], paired = FALSE)

```

## Read in and analyse task behavioural data

Behavioural task data includes responses the participants made during the task, i.e. reaction times and accuracy for decision tasks, or the number of words produced for speech generation tasks.

The following chunk reports summary statistics for these behavioural measures and tests whether there are any behavioural differences between left and right handers. (Spoiler alert: there aren't.)

```{r behaviouraldata}
behavdat_A2     <- read.csv('https://osf.io/wznbv/download') # Downloads A2_Behavioural_Data.csv from OSF Project
behavdat_Bangor <- read.csv('A2_Behavioural_Data_Bangor.csv') # this file is renamed; was A2_Results_Bangor.xlsx
colnames(behavdat_A2)[1] <- 'ID'
behavdat <- rbind(behavdat_A2,behavdat_Bangor)

# Only include participants in particdat
behavdat <- behavdat[which(behavdat$ID %in% particdat$ID), ]

# Concatenate with handedness
behavdat <- cbind(behavdat, handedness = particdat$handedness)
#NB Do not need to specify exclusions by sample or handedness here.
#Participant ID has already incorporated there

# Fix order of columns
behavdat <- behavdat %>% dplyr::select(handedness, A1.Words, A2.Words, A1.Omit, A2.Omit,
                   B1.Acc, B2.Acc, B1.RT, B2.RT, B1.Omit, B2.Omit,
                   C1.Acc, C2.Acc, C1.RT, C2.RT, C1.Omit, C2.Omit,
                   D1.Words, D2.Words, D1.Omit, D2.Omit,
                   E1.Acc, E2.Acc, E1.RT, E2.RT, E1.Omit, E2.Omit,
                   F1.Acc, F2.Acc, F1.RT, F2.RT, F1.Omit, F2.Omit)

# Recalculate the number of omitted trials as a percentage
omit.cols<- grep('*.Omit',colnames(behavdat))
nevents <- c(15, 15, 90, 90, # task A1, A2, B1, B2
             90, 90, 15, 15, # tasks C1, C2, D1, D2
             90, 90, 45, 45) # tasks E1, E2, F1, F2
for (i in 1:length(omit.cols)){
tmp <- behavdat[ , omit.cols[i]] / nevents[i] * 100 
behavdat[ , omit.cols[i]] <- round(tmp, 2)
}

# # Recalculate the RT data in ms rather than seconds
# rt.cols<-grep('*.RT', colnames(behavdat))
# behavdat[ , rt.cols] <- behavdat[ , rt.cols] * 1000

behav_means_LH <- round(colMeans(behavdat[which(behavdat$handedness=='L'),-1], na.rm = TRUE), 2)
behav_means_RH <- round(colMeans(behavdat[which(behavdat$handedness=='R'),-1], na.rm = TRUE), 2)

behav_sd_LH <- apply(behavdat[which(behavdat$handedness=='L') , -1], 2, function(x){
  round(sd(x, na.rm = TRUE), 2)
})
behav_sd_RH <- apply(behavdat[which(behavdat$handedness=='R') , -1], 2, function(x){
  round(sd(x, na.rm = TRUE), 2)
})

behav_table <- cbind(behav_means_LH, behav_sd_LH, behav_means_RH, behav_sd_RH)
colnames(behav_table) <- c('LH mean', 'LH sd', 'RH mean', 'RH sd')
kable(behav_table)

word.cols <- grep('*.Words', colnames(behavdat))
acc.cols<-grep('*.Acc', colnames(behavdat))
rt.cols<-grep('*.RT', colnames(behavdat))

# Do left and right handers show different levels of task performance?
cols_to_test <- c(word.cols, acc.cols, rt.cols)
behav_tests <- data.frame(
  'Measure' = colnames(behavdat)[cols_to_test],
  'df' = rep(NA, length(cols_to_test)),
  't' = rep(NA, length(cols_to_test)),
  'p' = rep(NA, length(cols_to_test))
)

for (i in 1:length(cols_to_test)){
  my_test <- t.test(behavdat[which(particdat$handcode == 1), cols_to_test[i]], 
                    behavdat[which(particdat$handcode == 2), cols_to_test[i]], 
                    paired = FALSE)
  behav_tests$df[i] <- my_test$parameter
  behav_tests$t[i] <- my_test$statistic
  behav_tests$p[i] <- my_test$p.value
}
corrected_alpha <- .05 / length(cols_to_test)
cat(paste0('Alpha corrected for ', length(cols_to_test), ' multiple comparisons = ', corrected_alpha))

if (length(which(behav_tests$p < corrected_alpha)) > 0){
  cat(paste0('Significant difference between left and right handers observed for: '))
  print(behav_tests$Measure[which(behav_tests$p < corrected_alpha)])
}
if (length(which(behav_tests$p < corrected_alpha)) == 0){
  cat(paste0('\nNo significant difference between left and right handers observed for number of words, RT or Accuracy on any task'))
  cat(paste0('p > ', round(min(behav_tests$p), 4), ' in all cases.'))
}

kable(behav_tests)
```

## Behavioural Test-rest reliablity

This chunk checks whether there are any test-retest differences in behavioural measures. Wilcoxon tests are used as measures are unlikely to be normally distributed.

```{r behav-retest}
# Test-retest comparisons for behavioural data
cols_to_test <- c(word.cols, acc.cols, rt.cols)
cols_to_test <- cols_to_test[seq(from = 1, to = length(cols_to_test)-1, by = 2)]
behav_measures <- length(cols_to_test)  # Number of tests performed

behav_retest <- data.frame(matrix(NA,nrow=behav_measures,ncol=3))
colnames(behav_retest)<-c('Measure','V','p')
behav_retest$Measure <- colnames(behavdat)[cols_to_test]

myrow <- 0
# Loop through measures
for (m in 1:behav_measures){
  myrow <- myrow+1
  col1 <- cols_to_test[m]
  col2 <- cols_to_test[m] + 1
  # Perform Wilcoxen test
  my_test <- wilcox.test(behavdat[ , col1],  # Session 1
                          behavdat[ , col2],  # Session 2
                          paired = TRUE) 
  # Organise output
  behav_retest$V[myrow] <- round(my_test$statistic, 2)
  behav_retest$p[myrow] <- round(my_test$p.value, 3)
}

# Report results
corrected_alpha <- .05 / behav_measures
sig_count <- length(which(behav_retest$p < corrected_alpha))
cat(paste('Number of tasks with significant test-retest behavioural differences: ', sig_count))
if (sig_count > 0){cat('\nCheck behav_retest for details')}

```

## Calculate means of LI values, check normality and create pirate plot

The fTCD data is analysed (in another script) to produce laterality indices (LI values) for each task in each session. The LI values are used subsequently in the SEM analysis.

The following chunk reports summary statistics and produces a plot of the LI values.

```{r LI_means, warning=FALSE}
# Modified script for ggpirate plot
source('geom_pirate_ZW.R')

# Create data frame for Shapiro Wilks test results
handedness <- c('Right Handed', 'Left Handed')
shapdf <- data.frame(matrix(NA, nrow=24, ncol=4))
colnames(shapdf) <- c('Task', 'Session', 'Hand', 'p')
myrow<-0 

# Normality tests and plots
for (i in 1:6){ # Loop through tasks
  my_fig_name <- paste0('Supp_Fig_1', LETTERS[i], '.png')
  png(my_fig_name, width=8, height=6, units="in", res=300)
  par(mfrow=c(2,4))
  
  for (j in 1:2){ # Loop through sessions
  offset<- 6*(j-1)
  
    for (h in c(2,1)){ # Loop through handedness (left first so it's on the left of the plot)
      myrow<-myrow+1
      handedness_text <- handedness[h]
      handedness_rows <- which(particdat$handcode == h)
      tempdata<-alltask[handedness_rows,(i+offset)]
      myshap<-shapiro.test(tempdata)
      
      # Histogram
      
      plot (density (tempdata, na.rm = TRUE),
            main = paste (handedness_text, '_', mylabels[(i + offset)]),
            xlim = c(-6, 8), ylim = c(0, 0.4))
      
      
      text(-2, 0.3, paste('mean = \n', round(mean(tempdata, na.rm = TRUE), 2)))
      
      # qqplot
      qqnorm(tempdata); qqline(tempdata, col = 2)
      text(1, 0, paste('Shapiro\np = ', round(myshap$p.value, 3)))
      shapdf$Task[myrow] <- LETTERS[i] # Clever! Swaps numbers 1:6 to letters A:F
      shapdf$Session[myrow] <- j
      shapdf$Hand[myrow] <- h
      shapdf$p[myrow] <- round(myshap$p.value, 3)
      
    } # Hand loop
  } # Session loop
  dev.off()
} # Task loop

  
# One-sample t-tests to compare LI to zero
LI_ttests<-data.frame(matrix(NA,nrow=24,ncol=10))
colnames(LI_ttests)<-c('Taskcode','Session','Hand','mean','sd','t','df','p','LI','lab')

LI_ttests$Session <- rep(c(1,2),6)
LI_ttests$Task <- rep(myshortlab,each=2)
LI_ttests$Hand <- rep(c(1,2),each=12)

myrow<-0 

for (h in c(1,2)){ # Loop through handedness
  handedness_rows <- which(particdat$handcode == h)
  
  for (t in 1:6){ # Loop through tasks
    
    for (s in 1:2){ # Loop through sessions
      myrow <- myrow + 1
      mycol <- t + ((s-1)*6) 
      
      # Perform t-test
      my_test <- t.test(alltask[handedness_rows, mycol], alternative='greater')
      
      # Organise output
      LI_ttests$Taskcode[myrow] <- LETTERS[t]
      LI_ttests$Session[myrow] <- s
      LI_ttests$Hand[myrow] <- handedness[h]
      LI_ttests$mean[myrow] <- round(mean(alltask[handedness_rows, mycol], na.rm = TRUE), 2)
      LI_ttests$sd[myrow] <- round(sd(alltask[handedness_rows, mycol], na.rm = TRUE), 2)
      LI_ttests$t[myrow] <-round(my_test$statistic,2)
      LI_ttests$df[myrow] <-my_test$parameter
      LI_ttests$p[myrow] <-round(my_test$p.value,3)
      LI_ttests$LI[myrow] <- max(alltask[handedness_rows, mycol],na.rm=TRUE)+1
      mylabel <- ''
      if(my_test$p.value<.05){mylabel <- "*"}
      if(my_test$p.value<.01){mylabel <- "**"}
      if(my_test$p.value<.001){mylabel <- "***"}
      LI_ttests$lab[myrow] <- mylabel
    } # Session loop
  } # Task loop
} # Hand loop

LI_ttests$Taskcode <- as.factor(LI_ttests$Taskcode)
LI_ttests$Session <- as.factor(LI_ttests$Session)
LI_ttests$Hand <- as.factor(LI_ttests$Hand)

# Collate LI data for pirate plot
ID_data <- data.frame(
  ID = as.factor(particdat$ID),
  Hand = as.factor(particdat$handedness))
pirate_data <- cbind(ID_data, alltaskall)
#colnames(pirate_data)[15:26] <- c('A1_cat', 'B1_cat', 'C1_cat', 'D1_cat', 'E1_cat', 'F1_cat',
#                                  'A2_cat', 'B2_cat', 'C2_cat', 'D2_cat', 'E2_cat', 'F2_cat')

LI_long <- melt(pirate_data, value.name = 'LI') #version with outliers 
LI_long$Session <- as.factor(c(rep(1, nsubj_final*6), rep(2, nsubj_final*6)))
LI_long$Task <- rep(rep(myshortlab, each=nsubj_final), 2)
LI_long$Taskcode <- rep(rep(c('A','B','C','D','E','F'), each = nsubj_final), 2)
levels(LI_long$Hand) <- c('Left Handed','Right Handed')

# Add laterality categories
category_data <- cbind(ID_data, alltasklat)
category_long <- melt(category_data)
colnames(category_long) <- c('ID','Hand','Task','Category')
category_long$Category[which(category_long$Category != 2)] <- 1
category_long$Category[which(category_long$Category == 2)] <- 0
category_long$Hand <- LI_long$Hand
category_long$Task <- rep(rep(c('A','B','C','D','E','F'), each = nsubj_final), 2)
category_long$Session <- as.factor(c(rep(1, nsubj_final*6), rep(2, nsubj_final*6)))
category_long$LI <- LI_long$LI
category_long$Category <- as.factor(category_long$Category)
category_long <- category_long[-which(is.na(category_long$Category)), ]
levels(category_long$Category) <- c(1, 16)

# Also identify excluded data points (NAs in alltask)
NA_data <- cbind(ID_data, alltask)
NA_long <- melt(NA_data, value.name = 'LI_NA')
NA_long[ , 5:8] <- LI_long[ , 4:7]
levels(NA_long$Hand) <- c('Left Handed','Right Handed')

#add dummy rows to make the plot jitter work
extra_data <- data.frame(matrix(20, nrow=2, ncol=14))
colnames(extra_data) <- c('ID','Hand',colnames(alltask))  
extra_data$ID <- as.factor('dummy')
extra_data$Hand <- as.factor(c('L','R'))
extra_long <- melt(extra_data, value.name = 'LI_NA')
extra_long$Session <- as.factor(c(rep(1, 2*6), rep(2, 2*6)))
extra_long$Task <- rep(rep(myshortlab, each=2), 2)
extra_long$Taskcode <- rep(rep(c('A','B','C','D','E','F'), each = 2), 2)
levels(extra_long$Hand) <- c('Left Handed','Right Handed')
extra_long$LI_NA <- NA
extra_long$LI <- NA

# Combine with NA_long, and select only rows with excluded datapoints
NA_long <- rbind(NA_long, extra_long)
NA_long <- NA_long[which(is.na(NA_long$LI_NA)), ]

# Make pirate plot
my_pirate = ggplot(data = LI_long,
                   mapping = aes(x = Taskcode,
                                 y = LI,
                                 colour = Session)) +
 geom_pirate_ZW(points_params = list(alpha = 0),
                 bars = FALSE,
                 #bars_params = list(colour = 'black'),
                 #violins_params = list(width = 3),
                 #cis_params = list(width = 3),
                 #lines_params = list(width = 3),
                 jitter_width = 0.4, show.legend=TRUE) +
  labs(y = 'LI Value', x = 'Task') +
  scale_y_continuous(breaks = seq(from = -6, to = 7, by = 1)) +
  theme_bw() +
  theme(legend.position = 'right', panel.grid.minor = element_blank(), panel.grid.major.x = element_blank()) +
  geom_hline(yintercept = 0) +
  facet_grid(.~Hand) +
  # Asterisks for significant LI values
  geom_text(data = LI_ttests, aes(x = Taskcode, group = Session, y = LI, label = lab),
            position = position_dodge(0.7), colour = 'black') +
  # Coded points for laterality categories
  geom_point(data = category_long, aes(x = Task, group = Session, y = LI, shape = Category),
             position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.7),
             size = 1.2, alpha = 0.8, na.rm = TRUE) +
  scale_shape_manual(values = c(1, 19), 
                     name = 'Lateralisation', labels = c('Non-lateralised', 'Lateralised')) +
  # Black points for outlier datapoints
  geom_point(data = NA_long, aes(x = Taskcode, group = Session, y = LI),
             position = position_dodge(0.7), colour = 'black', size = 1.4, pch=18)

print(my_pirate)

ggsave(filename = 'My_pirate.png', plot = my_pirate, width = 8, height = 4)

# Holy moly that was a lot of work for one plot
```


## LI Test-rest reliablity

This chunk checks whether there are any test-retest differences in LI values

```{r LI-retest}
# Test-retest comparisons of LI values
LI_retest <- data.frame(matrix(NA,nrow=12,ncol=5))
colnames(LI_retest)<-c('Hand','Task','t','df','p')
LI_retest$Hand <- rep(c(1,2),each=6)
LI_retest$Task <- rep(myshortlab,2)

myrow <- 0
# Loop through groups
for (h in 1:2) {
  handedness_rows <- which(particdat$handcode == h)
  # Loop through tasks
  for (t in 1:6){
    myrow <- myrow+1
    # Perform t-test
    my_test <- t.test(alltask[handedness_rows, t],    # Session 1
                      alltask[handedness_rows, t+6],  # Session 2
                      paired = TRUE)
    # Organise output
    LI_retest$t[myrow] <- round(my_test$statistic, 2)
    LI_retest$df[myrow] <- my_test$parameter
    LI_retest$p[myrow] <- round(my_test$p.value, 3)
  }
}

sig_count <- length(which(LI_retest$p < .05))
cat(paste('Number of tasks with significant test-retest LI differences: ', sig_count))
if (sig_count > 0){cat('\nCheck LI_retest for details')}

```


## LI correlation matrix


```{r corrheat,fig.height=6,figwidth=10}

ilist <- c(1,7,2,8,3,9,4,10,5,11,6,12)
both_cormats <- data.frame(matrix(data=NA, nrow=1, ncol=4))
colnames(both_cormats) <- c('Var1','Var2','cor','Hand')

for(h in 1:2){ # Loop through right and left handers
  handedness_rows <- which(particdat$handcode == h)
  
  # Select alltask data and perform correlations
  cormat<-round(cor(alltask[handedness_rows, ilist], use="pairwise.complete.obs", method="pearson"),2)
  rownames(cormat)<-c('A1','A2','B1','B2','C1','C2','D1','D2','E1','E2','F1','F2')
  colnames(cormat)<-c('A1','A2','B1','B2','C1','C2','D1','D2','E1','E2','F1','F2')
  
  # Use only the upper triangle of data (to avoid repetition)
  get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
  }
  upper_tri <- get_upper_tri(cormat)
  
  # Melt into long format
  melted_cormat <- melt(upper_tri, na.rm=T, value.name='cor')
  colnames(melted_cormat)[1:2]<-c('Var1','Var2') #names of cols 1 and 2
  melted_cormat$Hand <- h
  
  both_cormats <- rbind(both_cormats, melted_cormat)
}
both_cormats <- both_cormats[-1,]
both_cormats$Hand <- as.factor(both_cormats$Hand)
both_cormats$Hand <- factor(both_cormats$Hand, levels(both_cormats$Hand)[c(2,1)])
levels(both_cormats$Hand) <- c('Left Handed','Right Handed')

# Create correlation heatmap using ggplot
ggheatmap <- ggplot(data = both_cormats, aes(Var2, Var1, fill = cor)) +
  geom_tile(colour = "white") +
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1, 1), space = "Lab", 
                       name="Pearson Correlation") +
  theme_minimal() + 
  theme(axis.text.x = element_text(vjust = 1, size = 10, hjust = 0.5, colour = 'black'),
        axis.text.y = element_text(vjust = 0.5, size = 10, hjust = 1, colour = 'black')) +
  coord_fixed() +
  facet_grid(.~Hand)

#add some formatting
my_cormat <- ggheatmap + 
  geom_text(aes(Var2, Var1, label = cor), color = "black", size = 4) +
  theme(
    axis.title.x = element_blank(), axis.title.y = element_blank(),
    panel.grid.major = element_blank(), panel.border = element_rect(colour = 'black', fill = NA),
    #panel.background = element_rect(fill = 'grey'),
    axis.ticks = element_blank(),
    legend.position = 'bottom',
    legend.direction = "horizontal",
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 14),
    strip.text.x = element_text(size = 20),
    strip.background = element_rect(fill = 'grey90', colour = 'black')) +
  guides(fill = guide_colorbar(barwidth = 9, barheight = 1,
                               title.position = "top", title.hjust = 0.5))

print(my_cormat)

ggsave(filename = 'My_cormat.png', dpi=300, plot = my_cormat, width = 10, height = 6)
```


##Check reason for test-retest reliability issues in right handers

```{r retestscatter, warnings = FALSE}
scatter1 <- alltask[ , 1:6] %>% gather(key = Task, value = Session1)
scatter2 <- alltask[ , 7:12] %>% gather(key = Task, value = Session2)

scatterdata <- data.frame('Study' = as.factor(particdat$study), 'ID' = particdat$ID, 'Hand' = particdat$handedness,
                          'Session1' = scatter1$Session1, 'Session2' = scatter2$Session2, 
                          'Task' = rep(LETTERS[1:6], each = nsubj_final))
scatterdata$Task <- as.factor(scatterdata$Task)

myscatter <- ggplot(data = scatterdata, aes(x = Session1, y = Session2, colour = Hand)) +
  geom_point(alpha = 0.7) + theme_bw() + geom_abline(intercept = 0, slope = 1) + ylim(-6,6) + xlim(-6,6) + 
  facet_wrap(~Task) 
  #geom_text(aes(x = 3, y = -3, label = 'Testing...'))

print(myscatter)

ggsave(filename = 'My_scatter.png', dpi=300, plot = myscatter, width = 10, height = 6)
```


## Structural Equation Modeling

### Try with different order of variables

```{r reordertasks}
#Reassuring that reordering variables does not affect model fit
#However, it does affect the model structure.
#The first variable in the list will have fixed paths to factor A (1) and B (0)

if (tryreorder==1){ #See tryreorder toggle
  alltask<-alltask[,nuorder] #See nuorder toggle
  alltaskall<-alltaskall[,nuorder]
  mylabels<-mylabels[nuorder]
  myshortlab<-myshortlab[nuorder[1:length(myshortlab)]]
  mylonglab<-mylonglab[nuorder[1:length(mylonglab)]]
}
myfixed<-myshortlab[1]
```

### Question 1: 1 vs 2 Factors

Test SEM models with 1 or 2 factors.
Keep left and right handers separate to start so that we can see if the same model wins in both groups, and if the results are reliable (drop one validation) 

```{r SEM_1vs2}
#=================================================================================#
# Select RH data
RH_row <- which(particdat$handcode == 1)
dataRaw_RH <- mxData(observed = alltask[RH_row, ], type = 'raw')

#  Select LH data
LH_row <- which(particdat$handcode == 2)
dataRaw_LH <- mxData( observed=alltask[LH_row, ], type = "raw" )

#=================================================================================#
# One Factor Models

# Define Model1_RH
Model1RH <- umxRAM("Model1RH", data=dataRaw_RH, suffix = "_RH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6,"_RH"), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_RH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_RH"), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))

# Define Model1_LH
Model1LH <- umxRAM("Model1LH", data=dataRaw_LH, suffix = "_LH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6,"_LH"), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_LH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_LH"), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))

#=================================================================================#
# Two Factor Models

# Define Model2_RH
Model2RH <- umxRAM("Model2RH", data=dataRaw_RH, suffix = "_RH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6,"_RH"), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6,"_RH"), free = c(F,T,T,T,T,T), values = c(0,rep(1,5))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_RH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_RH"), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

# Define Model2_LH
Model2LH <- umxRAM("Model12H", data=dataRaw_LH, suffix = "_LH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6,"_LH"), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6,"_LH"), free = c(F,T,T,T,T,T), values = c(0,rep(1,5))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_LH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_LH"), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

#=================================================================================#
# Model comparison

# Right handers
mychitest_RH <- mxCompare(Model2RH, Model1RH)
mychitest_RH
# Left handers
mychitest_LH <- mxCompare(Model2LH, Model1LH)
mychitest_LH

```

Conclusion: The two factor model is the winner in both right and left handed groups, but the difference is marginal in right handers.
Next: Test reliability of the 2 factor solution using drop-one analysis.

## Check solution robustness with drop one approach and explore results

This chunk drops one subject in each iteration and runs Model 4 (single factor) and Model 5 (bifactor).

```{r dropone, message=FALSE, warning=FALSE,echo=TRUE,eval=FALSE,asis=FALSE}
#Set up model definition
factor_loadings_1 <- umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6))
factor_loadings_2 <- umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6), free = c(F,T,T,T,T,T), values = c(0,rep(1,5)))
factor_covariances <- umxPath(cov = c("F1", "F2"),fixedAt=0)
factor_variances_1 <- umxPath(var='F1', freeAt=1)
factor_variances_2 <- umxPath(var='F2', fixedAt=1)
residual_variances <- umxPath(var=mylabels, labels = paste0("var_",1:6), freeAt=1)
indicator_means <- umxPath(means=mylabels, labels = paste0("mean_",1:6), freeAt=1)
factor_means_1 <- umxPath(means=c('F1'),fixedAt = 0)
factor_means_2 <- umxPath(means=c('F1','F2'),fixedAt = 0)

#=================================================================================#
# Drop-one loop

#Use'drop one' approach - reduce the dataset by one on each run
for (group in 1:2){
  
  # Select subjects
  nsubs <- length(RH_row)
  if(group == 2){nsubs <- length(LH_row)}
  
  # Create dataframe to save the results
  dropone_results <- matrix(data = NA, nrow = nsubs, ncol = 5)

  for (thisdrop in 1:nsubs){
    
    myrows <- RH_row
    if(group ==2){myrows <- LH_row}
    
    dataRaw <- mxData(observed = alltask [myrows [-thisdrop], ], type="raw")
    
    # Estimate Factor 1 model
    myModel1 <- umxRAM("myModel1", data=dataRaw, 
                       factor_loadings_1, factor_variances_1, residual_variances, indicator_means, factor_means_1,autoRun=FALSE)
    mysum1<-mxRun(myModel1)
    summary.Model1 <- summary(mxRun(mysum1))
    
    # Estimate Factor 2 model
    myModel2 <- umxRAM('myModel2', data=dataRaw,
                       factor_loadings_1, factor_loadings_2, factor_covariances, factor_variances_1, factor_variances_2,
                       residual_variances, indicator_means, factor_means_2,autoRun = FALSE)
    mysum2<-mxRun(myModel2)
    summary.Model2 <- summary(mysum2)                  
    
    #Compare Models
    mcomp <- mxCompare(mysum2, mysum1)
    
    #Write results to dropone_results data frame
    dropone_results[thisdrop, 1] <- round(summary.Model1$BIC.Mx, 3)
    dropone_results[thisdrop, 2] <- round(summary.Model2$BIC.Mx, 3)
    dropone_results[thisdrop, 3] <- round(mcomp$diffLL[2], 3)
    dropone_results[thisdrop, 4] <- mcomp$diffdf[2]
    dropone_results[thisdrop, 5] <- round(mcomp$p[2], 5)

  }
  
    colnames(dropone_results) <- c('BIC_mod1','BIC_mod2','chi.diff','df.diff','p.diff')
    dropone_results<-data.frame(dropone_results)
    dropone_results$BIC_diff <- dropone_results$BIC_mod1 - dropone_results$BIC_mod2
    dropone_results$bestModel<-'one factor'
    w<-which(dropone_results$p.diff < .05 & dropone_results$BIC_diff > 0)
    dropone_results$bestModel[w]<-'bifactor'
    
  if (group == 1){dropone_results_RH <- dropone_results}
  if (group == 2){dropone_results_LH <- dropone_results}
  
}

```

### SEM Multigroup models: 2 factors.

Two factor multigroup models, comparing constrained and unconstrained models

```{r SEM_multigroup}
#=================================================================================#
# Constrained multigroup model where factor loadings are set to be the same in the two groups
Model2_unc_mg <- umxSuperModel("Model2_unconstrained", Model2RH, Model2LH)

#=================================================================================#
# Constrained multigroup model where factor loadings are set to be the same in the two groups

# Right handers
Model2RH_con <- umxRAM("Model2RH", data=dataRaw_RH, suffix = "_RH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6), free = c(F,T,T,T,T,T), values = c(0,rep(1,5))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_RH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_RH"), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

# Left handers
Model2LH_con <- umxRAM("Model12H", data=dataRaw_LH, suffix = "_LH",
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6), free = c(F,T,T,T,T,T), values = c(0,rep(1,5))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6,"_LH"), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6,"_LH"), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

Model2_con_mg <- umxSuperModel("Model2_constrained", Model2RH_con, Model2LH_con)

#=================================================================================#
# Comparison of unconstrained and constrained multigroup models

anova(Model2_unc_mg, Model2_con_mg)

```

Conclusion: For the 2 factor model, the unconstrained model IS significantly better than the constrained model, but the effect is small. The (cautious) conclusion is that for this model, there is a difference between the factor loadings for the left and right handed groups.

### Plotting results of the winning SEM model

The remaining analyses will focus on the model with the strongest evidence: 2 factor model where factor loadings could differ between left and right handed groups (unconstrained)

```{r FactorPlots2,fig.width=10,fig.height=10,echo=TRUE}
#=================================================================================#
# Select Factor 1 loadings for plotting 
# The parameters are from the multigroup model, but the separate model ones are the same)
# The right handed group comes first
winning_summary <- summary(Model2_unc_mg)

real_est_path <- winning_summary$parameters$Estimate
real_est_se <- winning_summary$parameters$Std.Error
mylowCI <- real_est_path - 1.96*real_est_se
myhighCI <- real_est_path + 1.96*real_est_se

# NB: In this data, the rows are as follows:
# 1-5:    Factor 1 loadings, RH
# 6-10:   Factor 2 loadings, RH
# 11-16:  Residual variances, RH
# 17:     Factor 1 variance, RH
# 18-23:  Means, RH

# 24-28:  Factor 1 loadings, LH
# 29-33:   Factor 2 loadings, LH
# 34-39:  Residual variances, LH
# 40:     Factor 1 variance, LH
# 41-46:  Means, LH

# Bear in mind that if you change the winning model, the indices below will also need to change!!

Factor1_plot_data = data.frame(
  'Task' = rep(c('A','B','C','D','E','F'), 2),
  'Group' = rep(c('Left Handed', 'Right Handed'), each = 6), # Left handers first to make the plot work
  'Loading' = c(real_est_path[24:26],1,real_est_path[27:28], # Factor 1 loadings, LH
                real_est_path[1:3],1,real_est_path[4:5]),    # Factor 1 loadings, RH
  'lowCI' = c(mylowCI[24:26],1,mylowCI[27:28],               # Factor 1 low CI, LH
              mylowCI[1:3],1,mylowCI[4:5]),                  # Factor 1 low CI, RH
  'highCI' = c(myhighCI[24:26],1,myhighCI[27:28],            # Factor 1 high CI, LH
               myhighCI[1:3],1,myhighCI[4:5])                # Factor 1 high CI, RH
)
Factor1_plot_data$Task <- factor(Factor1_plot_data$Task, levels = c('A','B','C','D','E','F'))
Factor1_plot_data$Group <- factor(Factor1_plot_data$Group)
Factor1_plot_data$Factor<-rep('Factor 1',length(Factor1_plot_data[,1]))

#=================================================================================#
# Select Factor 2 loadings for plotting
Factor2_plot_data = data.frame(
  'Task' = rep(c('A','B','C','D','E','F'), 2),
  'Group' = rep(c('Left Handed','Right Handed'), each = 6),
  'Loading' = c(real_est_path[29:31],0,real_est_path[32:33], # Left Handers factor1 loadings
                real_est_path[6:8],0,real_est_path[9:10]), # Right Handers factor 1 loadings
  'lowCI' = c(mylowCI[29:31],0,mylowCI[32:33], # Left Handers factor1 low CI
              mylowCI[6:8],0,mylowCI[9:10]), # Right Handers factor1 low CI
  'highCI' = c(myhighCI[29:31],0,myhighCI[32:33],
               myhighCI[6:8],0,myhighCI[9:10])
)

Factor2_plot_data$Task <- factor(Factor2_plot_data$Task, levels = c('A','B','C','D','E','F'))
Factor2_plot_data$Group <- factor(Factor2_plot_data$Group)
Factor2_plot_data$Factor<-rep('Factor 2',length(Factor2_plot_data[,1]))

Factor_plot_data<-rbind(Factor1_plot_data,Factor2_plot_data)
Factor_plot_data$Factor<-as.factor(Factor_plot_data$Factor)
#=================================================================================#
# Plot Factor 2 loadings
my_factor_both <- ggplot(Factor_plot_data, aes(x = Task, y = Loading, fill = Task)) +
  geom_boxplot(lower = Factor_plot_data$lowCI, upper = Factor_plot_data$highCI) +
  ylim(-1,2) +
  theme_bw() +
  geom_hline(yintercept = 0) +
  ylab('Factor Loadings') +
  facet_grid(Factor~Group) + theme(legend.position='none')

print(my_factor_both)
ggsave(filename = 'My_factors.png', dpi=300, plot = my_factor_both, width = 6, height = 5) 
```


## Make factor scores and plot them

```{r makefacscores}

#This is with loadings - but it makes little difference
#In weighted sum use original data, including excluded datapoints (alltaskall) to avoid losing subjects from this

#=================================================================================#
# Right handers

# Select factor loadings for right handers
allf1_RH <- c(1, real_est_path[1:5]) # Factor 1, RH
allf2_RH <- c(0, real_est_path[6:10]) # Factor 2, RH

# Multiply LI values by factor loading and sum to give factor scores for each individual
for (i in 1:length(RH_row)){
  # Factor 1
  alltask$f1score[RH_row[i]] <- alltaskall[RH_row[i],1] * allf1_RH[1] + 
                        alltaskall[RH_row[i],2] * allf1_RH[2] +
                        alltaskall[RH_row[i],3] * allf1_RH[3]+
                        alltaskall[RH_row[i],4] * allf1_RH[4]+
                        alltaskall[RH_row[i],5] * allf1_RH[5]+
                        alltaskall[RH_row[i],6] * allf1_RH[6]+
                        alltaskall[RH_row[i],7] * allf1_RH[1]+
                        alltaskall[RH_row[i],8] * allf1_RH[2]+
                        alltaskall[RH_row[i],9] * allf1_RH[3]+
                        alltaskall[RH_row[i],10] * allf1_RH[4]+
                        alltaskall[RH_row[i],11] * allf1_RH[5]+
                        alltaskall[RH_row[i],12] * allf1_RH[6]
  # Factor 2
  alltask$f2score[RH_row[i]] <- alltaskall[RH_row[i],1] * allf2_RH[1]+
                        alltaskall[RH_row[i],2] * allf2_RH[2]+
                        alltaskall[RH_row[i],3] * allf2_RH[3]+
                        alltaskall[RH_row[i],4] * allf2_RH[4]+
                        alltaskall[RH_row[i],5] * allf2_RH[5]+
                        alltaskall[RH_row[i],6] * allf2_RH[6]+
                        alltaskall[RH_row[i],7] * allf2_RH[1]+
                        alltaskall[RH_row[i],8] * allf2_RH[2]+
                        alltaskall[RH_row[i],9] * allf2_RH[3]+
                        alltaskall[RH_row[i],10] * allf2_RH[4]+
                        alltaskall[RH_row[i],11] * allf2_RH[5]+
                        alltaskall[RH_row[i],12] * allf2_RH[6]
}
#check for bivariate outliers
facmod_RH <- lm(alltask$f1score[RH_row] ~ alltask$f2score[RH_row])
alltask$cookdist <- 0
alltask$cookdist[RH_row] <- cooks.distance(facmod_RH)

#=================================================================================#
# Left handers
allf1_LH <- c(1, real_est_path[24:28]) # Factor 1, LH
allf2_LH <- c(0, real_est_path[29:33]) # Factor 2, LH

for (i in 1:length(LH_row)){
  # Factor 1
  alltask$f1score[LH_row[i]] <- alltaskall[LH_row[i],1] * allf1_LH[1] + 
                        alltaskall[LH_row[i],2] * allf1_LH[2] +
                        alltaskall[LH_row[i],3] * allf1_LH[3]+
                        alltaskall[LH_row[i],4] * allf1_LH[4]+
                        alltaskall[LH_row[i],5] * allf1_LH[5]+
                        alltaskall[LH_row[i],6] * allf1_LH[6]+
                        alltaskall[LH_row[i],7] * allf1_LH[1]+
                        alltaskall[LH_row[i],8] * allf1_LH[2]+
                        alltaskall[LH_row[i],9] * allf1_LH[3]+
                        alltaskall[LH_row[i],10] * allf1_LH[4]+
                        alltaskall[LH_row[i],11] * allf1_LH[5]+
                        alltaskall[LH_row[i],12] * allf1_LH[6]
  # Factor 2
  alltask$f2score[LH_row[i]] <- alltaskall[LH_row[i],1] * allf2_LH[1]+
                        alltaskall[LH_row[i],2] * allf2_LH[2]+
                        alltaskall[LH_row[i],3] * allf2_LH[3]+
                        alltaskall[LH_row[i],4] * allf2_LH[4]+
                        alltaskall[LH_row[i],5] * allf2_LH[5]+
                        alltaskall[LH_row[i],6] * allf2_LH[6]+
                        alltaskall[LH_row[i],7] * allf2_LH[1]+
                        alltaskall[LH_row[i],8] * allf2_LH[2]+
                        alltaskall[LH_row[i],9] * allf2_LH[3]+
                        alltaskall[LH_row[i],10] * allf2_LH[4]+
                        alltaskall[LH_row[i],11] * allf2_LH[5]+
                        alltaskall[LH_row[i],12] * allf2_LH[6]
}
#check for bivariate outliers
facmod_LH <- lm(alltask$f1score[LH_row] ~ alltask$f2score[LH_row])
alltask$cookdist[LH_row] <- cooks.distance(facmod_LH)


plot(alltask$cookdist, col=particdat$handcode, pch=16, ylab = 'Cooks Distance', xlab = 'Participant')
w<-which(alltask$cookdist>(4*mean(alltask$cookdist)))
abline(h=4*mean(alltask$cookdist), lty=2)
abline(v=37.5, lty=2)
text(x = 10, y = 0.14, labels = 'black = right handed\nred = left handed')
cat('Influential points are:') # These values are ROW NUMBERS not PARTICIPANT IDs
w
alltask$bivoutlier <-1
alltask$bivoutlier[w] <-16

# Make My_facscores.png plot, showing outliers and left-handers
png('My_facscores.png', width=6, height=5, units="in", res=300)
par(mar = c(4.5, 4.1, 1, 1))
plot(alltask$f1score,alltask$f2score, pch=alltask$bivoutlier, col=particdat$handcode, 
     xlab='Factor 1',ylab='Factor 2', xlim=c(-30, 30))
abline(v=0,lty=2)
abline(h=0,lty=2)
mycor_RH <- round(cor(alltask$f1score[RH_row], alltask$f2score[RH_row], use='pairwise.complete.obs'), 3)
mycor_LH <- round(cor(alltask$f1score[LH_row], alltask$f2score[LH_row], use='pairwise.complete.obs'), 3)
text(-14, 13, paste('Right Handers: r = ',mycor_RH))
text(-14, 20, paste('Left Handers: r = ',mycor_LH), col='red')
pData<-cbind(alltask,particdat)
covEllipses(x=pData[,c('f1score','f2score')], group=pData$handcode, 
            pooled=FALSE, add=TRUE, col=c("black","red"), labels="")

dev.off()
```


<!--
## Jacknife estimates of path SEs

Jacknife estimates considered for model SEs, which can be compared with standard method. The jacknife method uses the output from the drop-one analysis to look at distribution of estimates obtained with one subject omitted.

```{R jackknife,eval=FALSE,include=FALSE}
 # Calculates the jackknife estimates (bias corrected) and the bias. Then prints out corrected estimates vs the "real" estimates from the original model 5 run.
 #NB based on dropone_paths: this is matrix with nsub rows and 23 cols, with the columns corresponding to path estimates in the model.
 n=myrow

 #jacknife summary
 avgpathmeans<-colMeans(dropone_paths) #average estimate across all dropone runs
 jk_bias<-(n-1)*(avgpathmeans-real_est_path)

 jack_est<-(n*real_est_path)-((n-1)*avgpathmeans)
 pngname<-paste0('jacknifeplot_fix',myfixed,'.png')
png(pngname, width=4, height=4, units="in", res=300)

 plot(real_est_path,jack_est)
 dev.off()

 # calculates the jackknife SE estimates to allow us to calculate the CI.

 mycol<-length(real_est_path)
 jack_SE<-vector(mode="numeric",length=mycol)
 for (i in 1:(mycol))
 {
   jack_SE[i]<-sqrt(((n-1)/n)*sum((dropone_paths[,i]-avgpathmeans[i])^2))
 }
 myres<-data.frame(real_est_path)
 colnames(myres)[1]<-'Estimate'
 myres$L_ci<-round(real_est_path-1.65*real_est_se,2)
 myres$U_ci<-round(real_est_path+1.65*real_est_se,2)
 myres$jack_Estimate<-round(jack_est,2)
 myres$jack_Std.Error<-round(jack_SE,2)
 myres$jk_L_ci<-round(jack_est-1.65*jack_SE,2)
 myres$jk_U_ci<-round(jack_est+1.65*jack_SE,2)
 myres$jk_bias<-round(jk_bias,2)
 myres$Estimate<-round(myres$Estimate,2)

 plot(myres$Estimate,myres$jack_Estimate,main ='Jacknife analysis')
 write.csv(myres,"jacknife_ests.csv")

```
-->

## Exploratory tests of handedness

```{r exploratory,echo=FALSE,message=FALSE,WARNING=FALSE}
#exploring various links with handedness

apa_PT<-function (test.object, tails = 2, sig.digits = 5, p.lb = 0.01) 
{
    statistic.id <- substr(names(test.object$statistic), start = 1, 
        stop = 1)
    p.value <- test.object$p.value
    if (tails == 1) {
        p.value <- p.value/2
    }
    if (p.value < p.lb) {
        p.display <- paste("p = ", round(p.value,sig.digits), " (", tails, "-tailed)", 
            sep = "")
    }
    if (p.value > p.lb) {
        p.display <- paste("p = ", round(p.value, sig.digits), 
            " (", tails, "-tailed)", sep = "")
    }
    add.par <- ""
    if (grepl("product-moment", test.object$method)) {
        estimate.display <- paste("r = ", round(test.object$estimate, 
            sig.digits), ", ", sep = "")
    }
    if (grepl("Chi", test.object$method)) {
        estimate.display <- ""
        add.par <- paste(", N = ", sum(test.object$observed), 
            sep = "")
    }
    if (grepl("One Sample t-test", test.object$method)) {
        estimate.display <- paste("mean = ", round(test.object$estimate, 
            sig.digits), ", ", sep = "")
    }
    if (grepl("Two Sample t-test", test.object$method)) {
        estimate.display <- paste("mean difference = ", round(test.object$estimate[2] - 
            test.object$estimate[1], sig.digits), ", ", sep = "")
    }
    return(paste(estimate.display, statistic.id, "(", round(test.object$parameter, 
        sig.digits), add.par, ") = ", round(test.object$statistic, 
        sig.digits), ", ", p.display, sep = ""))
}


# Calculate difference between SentGen minus ListGen (averaged over both sessions)
mydiff<-(alltaskall$SentGen1+alltaskall$SentGen2)/2-(alltaskall$ListGen1+alltaskall$ListGen2)/2

particdat$handcode<-as.factor(particdat$handcode)
levels(particdat$handcode)<-c('R','L')

# Does this difference vary with handedness?
cat('Does this difference vary with handedness?','\n')
cat(apa_PT(t.test(mydiff~particdat$handcode)),'\n')
plot(mydiff~particdat$handcode,main=apa_PT(t.test(mydiff~particdat$handcode)),xlab='Hand',ylab='Difference score')
cat('\n')
# Which other tasks vary with handedness?
cat('Which other tasks vary with handedness?','\n')

taskA_LG<-(alltaskall$ListGen1+alltaskall$ListGen2)/2
cat('Task A: ',apa_PT(t.test(taskA_LG~particdat$handcode)),'\n')
plot(taskA_LG~particdat$handcode,main=apa_PT(t.test(taskA_LG~particdat$handcode)),xlab='Hand',ylab='Difference score')

taskB_PD<-(alltaskall$PhonDec1+alltaskall$PhonDec2)/2
cat('Task B: ',apa_PT(t.test(taskB_PD~particdat$handcode)),'\n')
plot(taskB_PD~particdat$handcode,main=apa_PT(t.test(taskB_PD~particdat$handcode)),xlab='Hand',ylab='Difference score')

taskC_SD<-(alltaskall$SemDec1+alltaskall$SemDec2)/2
cat('Task C: ', apa_PT(t.test(taskC_SD~particdat$handcode)),'\n')
plot(taskC_SD~particdat$handcode,main=apa_PT(t.test(taskC_SD~particdat$handcode)),xlab='Hand',ylab='Difference score')

taskD_SG<-(alltaskall$SentGen1+alltaskall$SentGen2)/2
cat('Task D: ',apa_PT(t.test(taskD_SG~particdat$handcode)),'\n')
plot(taskD_SG~particdat$handcode,main=apa_PT(t.test(taskD_SG~particdat$handcode)),xlab='Hand',ylab='Difference score')

taskE_SC<-(alltaskall$SentComp1+alltaskall$SentComp2)/2
cat('Task E: ', apa_PT(t.test(taskE_SC~particdat$handcode)),'\n')
plot(taskE_SC~particdat$handcode,main=apa_PT(t.test(taskE_SC~particdat$handcode)),xlab='Hand',ylab='Difference score')

taskF_JD<-(alltaskall$Jabber1+alltaskall$Jabber2)/2
cat('Task F: ', apa_PT(t.test(taskF_JD~particdat$handcode)),'\n')
plot(taskF_JD~particdat$handcode,main=apa_PT(t.test(taskF_JD~particdat$handcode)),xlab='Hand',ylab='Difference score')
cat('\n')
# Do factor scores vary with handedness?
cat('Do factor scores vary with handedness?','\n')
cat('FACTOR 1: ', apa_PT(t.test(alltask$f1score~particdat$handcode)),'\n')
cat('FACTOR 2: ', apa_PT(t.test(alltask$f2score~particdat$handcode)),'\n')
cat('\n')

# # Count how many tasks a subject is left lateralised for
# for (i in 1:nrow(alltask)){
# 
#   
#   alltask$Nleftlat[i]<-length(which(c(taskA_LG[i], taskB_PD[i], taskC_SD[i],
#                                       taskD_SG[i], taskE_SC[i], taskF_JD[i])>0))
# }

# Does the number of left lateralised tasks per participant vary with handedness?
# cat('Does the number of left lateralised tasks per participant vary with handedness?','\n')
# kable(table(alltask$Nleftlat,particdat$handcode))
# cat(apa_PT(t.test(alltask$Nleftlat~particdat$handcode)),'\n')

  
  # # Not sure what this is doing....
  # alltask$handcode<-particdat$handcode
  # alltaskhand<-alltask[order(alltask$f1score),]
  # alltaskhand$lowf1<-0
  # w<-which(alltaskhand$f1score<0)
  # alltaskhand$lowf1[w]<-1
  # alltaskhand$consistent<-0
  # w<-c(which(alltaskhand$Nleftlat==6),which(alltaskhand$Nleftlat==0))
  # alltaskhand$consistent[w]<-1


```


##Session information

```{r sessinfo}
sessionInfo()

```