---
title: "Laterality_Paper2"
author: "Zoe Woodhead & Paul Thompson"
date: "12/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction


## Set variables and load packages

```{r settings, warning=FALSE, message=FALSE}
########### Set toggles before running! ################################################################

# These toggles determine the parameters used in the analysis
Fonly             <- 0 # Set to 1 for females only. MANUSCRIPT SETTING = 0
Init30only        <- 0 # Set to 1 to include just the initial preregistered group (23 R and 7 L hander). MANUSCRIPT SETTING = 0
tryreorder        <- 1 # Set to 1 to change the fixed path in the SEM model. MANUSCRIPT SETTING = 1
nuorder           <-   # Sets the new order of tasks. The task listed first (and seventh) will be fixed.
 c(4,1,2,3,5,6,10,7,8,9,11,12) # Sentence generation fixed. MANUSCRIPT SETTING: c(4,1,2,3,5,6,10,7,8,9,11,12)
remove.Ntrial     <- 1 # Set to 1 to run exclusion of those with < 12 good trials. MANUSCRIPT SETTING = 1

########################################################################################################

#Needs OpenMx, which you get with following command (not CRAN)
#source('https://openmx.ssri.psu.edu/software/getOpenMx.R')
require(tidyverse)
require(OpenMx)
require(umx)
require(stargazer) #simple commands for nice tables
require(semTools) #for fit measures
#library(DiagrammeR) #for the diagram
require(stringr)
require(data.table)
library('devtools')
library("reshape2")
library("yarrr")
#library(DiagrammeRsvg)
library(magrittr)
library(svglite)
library(rsvg)
library(knitr)
library(dmm) #added for 'unfactor' command : nb this messes up some dplyr commands, need to specify dplyr explicitly, e.g. dplyr::select for 'select' command.
# On first use, please also install ggpirate as follows:
# devtools::install_github("mikabr/ggpirate")
library(ggpirate)
library(heplots)
```


# Structural Equation Modeling

## Simulate data

```{r sim_dat}
#========================================================================#
# simulate multivariate normal data to test ESEM model on three outcomes.#
#========================================================================#

# 12-02-2020

library(MASS)

sig1 <- matrix(c(1,	0.7,	0,	0,	0,	0,
                 0.7, 1, 0, 0, 0, 0,
                 0, 0, 1, 0.7, 0, 0,
                 0, 0, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_null <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig1)

#========================================================================#

sig2 <- matrix(c(1,	0.7,	0.4,	0.4,	0,	0,
                 0.7, 1, 0.4, 0.4, 0, 0,
                 0.4, 0.4, 1, 0.7, 0, 0,
                 0.4, 0.4, 0.7, 1, 0, 0,
                 0,0,0,0,1,0.7,
                 0,0,0,0,0.7,1),6,6,byrow=TRUE)

data_language <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig2)

#========================================================================#

sig3 <- matrix(c(1,	0.7, 0.4,	0.4, 0.4, 0.4,
                 0.7, 1, 0.4, 0.4, 0.4, 0.4,
                 0.4, 0.4, 1, 0.7, 0.4, 0.4,
                 0.4, 0.4, 0.7, 1, 0.4, 0.4,
                 0.4,0.4,0.4,0.4,1,0.7,
                 0.4,0.4,0.4,0.4,0.7,1),6,6,byrow=TRUE)

data_genLAT <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig3)

#========================================================================#

sig3A <- matrix(c(1,	0.4, 0.4,	0.4, 0.4, 0.4,
                 0.4, 1, 0.4, 0.4, 0.4, 0.4,
                 0.4, 0.4, 1, 0.4, 0.4, 0.4,
                 0.4, 0.4, 0.4, 1, 0.4, 0.4,
                 0.4,0.4,0.4,0.4,1,0.4,
                 0.4,0.4,0.4,0.4,0.4,1),6,6,byrow=TRUE)

data_genLAT <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig3)
data_genLAT2 <- mvrnorm(n=300, mu = c(5,5,5,5,5,5), Sigma=sig3A)

data_null<-as.data.frame(data_null)
data_language<-as.data.frame(data_language)
data_genLAT<-as.data.frame(data_genLAT)
data_genLAT2<-as.data.frame(data_genLAT2)

names(data_null)<-names(data_language)<-names(data_genLAT)<-names(data_genLAT2)<-c("dichotic1","dichotic2","rhyme1","rhyme2","faces1","faces2")

data_null<-data_null[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_language<-data_language[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_genLAT<-data_genLAT[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]
data_genLAT2<-data_genLAT2[,c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")]

#========================================================================#
```

## Null data model

### Question 1: 1 vs 2 Factors

Test SEM models with 1 or 2 factors.


```{r NULL_SEM_1vs2}

#=================================================================================#
# One Factor Models

mylabels<-c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")

# Define Model1
Model1 <- umxRAM("Model1", data=data_null,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))


#=================================================================================#
# Two Factor Models

# Define Model2
Model2 <- umxRAM("Model2", data=data_null,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

#=================================================================================#
# Model comparison

mychitest <- mxCompare(Model2, Model1)
mychitest


```


### Check solution robustness with drop one approach and explore results - NULL

This chunk drops one subject in each iteration and runs Model 4 (single factor) and Model 5 (bifactor).

```{r dropone_null, message=FALSE, warning=FALSE,echo=TRUE,eval=FALSE,asis=FALSE}
#Set up model definition
factor_loadings_1 <- umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3))
factor_loadings_2 <- umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2)))
factor_covariances <- umxPath(cov = c("F1", "F2"),fixedAt=0)
factor_variances_1 <- umxPath(var='F1', freeAt=1)
factor_variances_2 <- umxPath(var='F2', fixedAt=1)
residual_variances <- umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1)
indicator_means <- umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1)
factor_means_1 <- umxPath(means=c('F1'),fixedAt = 0)
factor_means_2 <- umxPath(means=c('F1','F2'),fixedAt = 0)

#=================================================================================#
# Drop-one loop

#Use'drop one' approach - reduce the dataset by one on each run

  # Select subjects
  nsubs <- length(data_null[,1])
  
  
  # Create dataframe to save the results
  dropone_results <- matrix(data = NA, nrow = nsubs, ncol = 5)
  
  for (thisdrop in 1:nsubs){
    
    dataRaw <- mxData(observed = data_null[-thisdrop, ], type="raw")
    
    # Estimate Factor 1 model
    myModel1 <- umxRAM("myModel1", data=dataRaw, 
                       factor_loadings_1, factor_variances_1, residual_variances, indicator_means, factor_means_1,autoRun=FALSE)
    mysum1<-mxRun(myModel1)
    summary.Model1 <- summary(mxRun(mysum1))
    
    # Estimate Factor 2 model
    myModel2 <- umxRAM('myModel2', data=dataRaw,
                       factor_loadings_1, factor_loadings_2, factor_covariances, factor_variances_1, factor_variances_2,
                       residual_variances, indicator_means, factor_means_2,autoRun = FALSE)
    mysum2<-mxRun(myModel2)
    summary.Model2 <- summary(mysum2)                  
    
    #Compare Models
    mcomp <- mxCompare(mysum2, mysum1)
    
    #Write results to dropone_results data frame
    dropone_results[thisdrop, 1] <- round(summary.Model1$BIC.Mx, 3)
    dropone_results[thisdrop, 2] <- round(summary.Model2$BIC.Mx, 3)
    dropone_results[thisdrop, 3] <- round(mcomp$diffLL[2], 3)
    dropone_results[thisdrop, 4] <- mcomp$diffdf[2]
    dropone_results[thisdrop, 5] <- round(mcomp$p[2], 5)

  }
  
    colnames(dropone_results) <- c('BIC_mod1','BIC_mod2','chi.diff','df.diff','p.diff')
    dropone_results<-data.frame(dropone_results)
    dropone_results$BIC_diff <- dropone_results$BIC_mod1 - dropone_results$BIC_mod2
    dropone_results$bestModel<-'one factor'
    w<-which(dropone_results$p.diff < .05 & dropone_results$BIC_diff > 0)
    dropone_results$bestModel[w]<-'bifactor'
    
  dropone_results_null<-dropone_results

```

## Language data model

### Question 1: 1 vs 2 Factors

Test SEM models with 1 or 2 factors.


```{r Lang_SEM_1vs2}

#=================================================================================#
# One Factor Models

mylabels<-c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")

# Define Model1
Model1 <- umxRAM("Model1", data=data_language,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))


#=================================================================================#
# Two Factor Models

# Define Model2
Model2 <- umxRAM("Model2", data=data_language,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

#=================================================================================#
# Model comparison

mychitest2 <- mxCompare(Model2, Model1)
mychitest2


```

### Check solution robustness with drop one approach and explore results - LANGUAGE

This chunk drops one subject in each iteration and runs Model 4 (single factor) and Model 5 (bifactor).

```{r dropone_lang, message=FALSE, warning=FALSE,echo=TRUE,eval=FALSE,asis=FALSE}
#Set up model definition
factor_loadings_1 <- umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3))
factor_loadings_2 <- umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2)))
factor_covariances <- umxPath(cov = c("F1", "F2"),fixedAt=0)
factor_variances_1 <- umxPath(var='F1', freeAt=1)
factor_variances_2 <- umxPath(var='F2', fixedAt=1)
residual_variances <- umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1)
indicator_means <- umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1)
factor_means_1 <- umxPath(means=c('F1'),fixedAt = 0)
factor_means_2 <- umxPath(means=c('F1','F2'),fixedAt = 0)

#=================================================================================#
# Drop-one loop

#Use'drop one' approach - reduce the dataset by one on each run

  # Select subjects
  nsubs <- length(data_language[,1])
  
  
  # Create dataframe to save the results
  dropone_results <- matrix(data = NA, nrow = nsubs, ncol = 5)
  
  for (thisdrop in 1:nsubs){
    
    dataRaw <- mxData(observed = data_language[-thisdrop, ], type="raw")
    
    # Estimate Factor 1 model
    myModel1 <- umxRAM("myModel1", data=dataRaw, 
                       factor_loadings_1, factor_variances_1, residual_variances, indicator_means, factor_means_1,autoRun=FALSE)
    mysum1<-mxRun(myModel1)
    summary.Model1 <- summary(mxRun(mysum1))
    
    # Estimate Factor 2 model
    myModel2 <- umxRAM('myModel2', data=dataRaw,
                       factor_loadings_1, factor_loadings_2, factor_covariances, factor_variances_1, factor_variances_2,
                       residual_variances, indicator_means, factor_means_2,autoRun = FALSE)
    mysum2<-mxRun(myModel2)
    summary.Model2 <- summary(mysum2)                  
    
    #Compare Models
    mcomp <- mxCompare(mysum2, mysum1)
    
    #Write results to dropone_results data frame
    dropone_results[thisdrop, 1] <- round(summary.Model1$BIC.Mx, 3)
    dropone_results[thisdrop, 2] <- round(summary.Model2$BIC.Mx, 3)
    dropone_results[thisdrop, 3] <- round(mcomp$diffLL[2], 3)
    dropone_results[thisdrop, 4] <- mcomp$diffdf[2]
    dropone_results[thisdrop, 5] <- round(mcomp$p[2], 5)

  }
  
    colnames(dropone_results) <- c('BIC_mod1','BIC_mod2','chi.diff','df.diff','p.diff')
    dropone_results<-data.frame(dropone_results)
    dropone_results$BIC_diff <- dropone_results$BIC_mod1 - dropone_results$BIC_mod2
    dropone_results$bestModel<-'one factor'
    w<-which(dropone_results$p.diff < .05 & dropone_results$BIC_diff > 0)
    dropone_results$bestModel[w]<-'bifactor'
    
  dropone_results_Lang<-dropone_results

```

## General Laterality data model

### Question 1: 1 vs 2 Factors

Test SEM models with 1 or 2 factors.


```{r GenLAT_SEM_1vs2}

#=================================================================================#
# One Factor Models

mylabels<-c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")

# Define Model1
Model1 <- umxRAM("Model1", data=data_genLAT,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))


#=================================================================================#
# Two Factor Models

# Define Model2
Model2 <- umxRAM("Model2", data=data_genLAT,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

#=================================================================================#
# Model comparison

mychitest3 <- mxCompare(Model2, Model1)
mychitest3


```

### Check solution robustness with drop one approach and explore results - general laterality

This chunk drops one subject in each iteration and runs Model 4 (single factor) and Model 5 (bifactor).

```{r dropone_genLat, message=FALSE, warning=FALSE,echo=TRUE,eval=FALSE,asis=FALSE}
#Set up model definition
factor_loadings_1 <- umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:3), free = c(F,T,T), values = rep(1,3))
factor_loadings_2 <- umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:3), free = c(F,T,T), values = c(0,rep(1,2)))
factor_covariances <- umxPath(cov = c("F1", "F2"),fixedAt=0)
factor_variances_1 <- umxPath(var='F1', freeAt=1)
factor_variances_2 <- umxPath(var='F2', fixedAt=1)
residual_variances <- umxPath(var=mylabels, labels = paste0("var_",1:3), freeAt=1)
indicator_means <- umxPath(means=mylabels, labels = paste0("mean_",1:3), freeAt=1)
factor_means_1 <- umxPath(means=c('F1'),fixedAt = 0)
factor_means_2 <- umxPath(means=c('F1','F2'),fixedAt = 0)

#=================================================================================#
# Drop-one loop

#Use'drop one' approach - reduce the dataset by one on each run

  # Select subjects
  nsubs <- length(data_genLAT[,1])
  
  
  # Create dataframe to save the results
  dropone_results <- matrix(data = NA, nrow = nsubs, ncol = 5)
  
  for (thisdrop in 1:nsubs){
    
    dataRaw <- mxData(observed = data_genLAT[-thisdrop, ], type="raw")
    
    # Estimate Factor 1 model
    myModel1 <- umxRAM("myModel1", data=dataRaw, 
                       factor_loadings_1, factor_variances_1, residual_variances, indicator_means, factor_means_1,autoRun=FALSE)
    mysum1<-mxRun(myModel1)
    summary.Model1 <- summary(mxRun(mysum1))
    
    # Estimate Factor 2 model
    myModel2 <- umxRAM('myModel2', data=dataRaw,
                       factor_loadings_1, factor_loadings_2, factor_covariances, factor_variances_1, factor_variances_2,
                       residual_variances, indicator_means, factor_means_2,autoRun = FALSE)
    mysum2<-mxRun(myModel2)
    summary.Model2 <- summary(mysum2)                  
    
    #Compare Models
    mcomp <- mxCompare(mysum2, mysum1)
    
    #Write results to dropone_results data frame
    dropone_results[thisdrop, 1] <- round(summary.Model1$BIC.Mx, 3)
    dropone_results[thisdrop, 2] <- round(summary.Model2$BIC.Mx, 3)
    dropone_results[thisdrop, 3] <- round(mcomp$diffLL[2], 3)
    dropone_results[thisdrop, 4] <- mcomp$diffdf[2]
    dropone_results[thisdrop, 5] <- round(mcomp$p[2], 5)

  }
  
    colnames(dropone_results) <- c('BIC_mod1','BIC_mod2','chi.diff','df.diff','p.diff')
    dropone_results<-data.frame(dropone_results)
    dropone_results$BIC_diff <- dropone_results$BIC_mod1 - dropone_results$BIC_mod2
    dropone_results$bestModel<-'one factor'
    w<-which(dropone_results$p.diff < .05 & dropone_results$BIC_diff > 0)
    dropone_results$bestModel[w]<-'bifactor'
    
  dropone_results_GenLat<-dropone_results

```

This is weird as I wouldn't expect that the model with all correlated factors should favour the bifactor??? See below to test model is oding as it should.


## General Laterality data model (adjusted correlation matrix to allow all six independent measures, i.e. no repeated measures and all 0.4 correlation with each other.)

### Question 1: 1 vs 2 Factors

Test SEM models with 1 or 2 factors.


```{r GenLAT2_SEM_1vs2}

#=================================================================================#
# One Factor Models

mylabels<-c("dichotic1","rhyme1","faces1","dichotic2","rhyme2","faces2")

# Define Model1
Model1 <- umxRAM("Model1", data=data_genLAT2,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   # Factor variances: F1 free
                   umxPath(var='F1', freeAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6), freeAt=1),
                   umxPath(means=c('F1'),fixedAt = 0))


#=================================================================================#
# Two Factor Models

# Define Model2
Model2 <- umxRAM("Model2", data=data_genLAT2,
                   # Factor loadings
                   umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6)),
                   umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6), free = c(F,T,T,T,T,T), values = c(0,rep(1,5))),
                   # Factor covariances: fixed to zero 
                   umxPath(cov = c("F1", "F2"),fixedAt=0),
                   # Factor variances: F1 free, F2 fixed at 1
                   umxPath(var='F1', freeAt=1),
                   umxPath(var='F2', fixedAt=1),
                   # Residual variances
                   umxPath(var=mylabels, labels = paste0("var_",1:6), freeAt=1),
                   # Means 
                   umxPath(means=mylabels, labels = paste0("mean_",1:6), freeAt=1),
                   umxPath(means=c('F1','F2'),fixedAt = 0))

#=================================================================================#
# Model comparison

mychitest3A <- mxCompare(Model2, Model1)
mychitest3A


```

### Check solution robustness with drop one approach and explore results - general language (adjusted correlation matrix to allow all six independent measures, i.e. no repeated measures and all 0.4 correlation with each other.)

This chunk drops one subject in each iteration and runs Model 4 (single factor) and Model 5 (bifactor).

```{r dropone_genLat2, message=FALSE, warning=FALSE,echo=TRUE,eval=FALSE,asis=FALSE}
#Set up model definition
factor_loadings_1 <- umxPath("F1", to = mylabels, labels = paste0("F1_to_",1:6), free = c(F,T,T,T,T,T), values = rep(1,6))
factor_loadings_2 <- umxPath("F2",to = mylabels, labels = paste0("F2_to_",1:6), free = c(F,T,T,T,T,T), values = c(0,rep(1,5)))
factor_covariances <- umxPath(cov = c("F1", "F2"),fixedAt=0)
factor_variances_1 <- umxPath(var='F1', freeAt=1)
factor_variances_2 <- umxPath(var='F2', fixedAt=1)
residual_variances <- umxPath(var=mylabels, labels = paste0("var_",1:6), freeAt=1)
indicator_means <- umxPath(means=mylabels, labels = paste0("mean_",1:6), freeAt=1)
factor_means_1 <- umxPath(means=c('F1'),fixedAt = 0)
factor_means_2 <- umxPath(means=c('F1','F2'),fixedAt = 0)

#=================================================================================#
# Drop-one loop

#Use'drop one' approach - reduce the dataset by one on each run

  # Select subjects
  nsubs <- length(data_genLAT2[,1])
  
  
  # Create dataframe to save the results
  dropone_results <- matrix(data = NA, nrow = nsubs, ncol = 5)
  
  for (thisdrop in 1:nsubs){
    
    dataRaw <- mxData(observed = data_genLAT2[-thisdrop, ], type="raw")
    
    # Estimate Factor 1 model
    myModel1 <- umxRAM("myModel1", data=dataRaw, 
                       factor_loadings_1, factor_variances_1, residual_variances, indicator_means, factor_means_1,autoRun=FALSE)
    mysum1<-mxRun(myModel1)
    summary.Model1 <- summary(mxRun(mysum1))
    
    # Estimate Factor 2 model
    myModel2 <- umxRAM('myModel2', data=dataRaw,
                       factor_loadings_1, factor_loadings_2, factor_covariances, factor_variances_1, factor_variances_2,
                       residual_variances, indicator_means, factor_means_2,autoRun = FALSE)
    mysum2<-mxRun(myModel2)
    summary.Model2 <- summary(mysum2)                  
    
    #Compare Models
    mcomp <- mxCompare(mysum2, mysum1)
    
    #Write results to dropone_results data frame
    dropone_results[thisdrop, 1] <- round(summary.Model1$BIC.Mx, 3)
    dropone_results[thisdrop, 2] <- round(summary.Model2$BIC.Mx, 3)
    dropone_results[thisdrop, 3] <- round(mcomp$diffLL[2], 3)
    dropone_results[thisdrop, 4] <- mcomp$diffdf[2]
    dropone_results[thisdrop, 5] <- round(mcomp$p[2], 5)

  }
  
    colnames(dropone_results) <- c('BIC_mod1','BIC_mod2','chi.diff','df.diff','p.diff')
    dropone_results<-data.frame(dropone_results)
    dropone_results$BIC_diff <- dropone_results$BIC_mod1 - dropone_results$BIC_mod2
    dropone_results$bestModel<-'one factor'
    w<-which(dropone_results$p.diff < .05 & dropone_results$BIC_diff > 0)
    dropone_results$bestModel[w]<-'bifactor'
    
  dropone_results_GenLat2<-dropone_results

```




##Session information

```{r sessinfo}
sessionInfo()

```